---
title: "Analysis for research paper No.1: Who bears what risk"
output: 
  html_notebook: 
    number_sections: yes
    toc: yes
    fig_caption: yes
editor_options: 
  chunk_output_type: console
---

```{r Global_settings, include=FALSE}

## Loading packages
source(here::here("libraries.R"))

theme_set(theme_yy())

dir_modelResults <- paste0(here::here(),"/Outputs/")
#dir_modelResults <- paste0(here::here(),"/Outputs_500sims/")
dir_outputs      <- paste0(here::here(),"/Analysis_paper1/figTbl_paper1/") 


# Global parameters for analysis
dr     <- 0.075 # discount rate
dr_low <- 0.03  # lower discount rate
infl   <- 0.02  # assumed inflation rate
# Nyear  <- 40    # Number of sim years for contribution analysis
cola_baseline <- 0.015

DC_EECrate <- 0.025
DC_ERCrate <- 0.028

```

```{r Loading_results, include = FALSE}

source(here::here("Analysis_loadingResults.R"))
# Outputs: 
   # results_all
   # run_labels



```



# Preparation




## Selecting runs for the paper 
```{r}

runs_paper <- c(
		baseline                 = "Baseline",
		
		cola_returnSmooth_calib2 = "Contingent COLA:\n5-year return",
		#cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		cola_FR_calib            = "Contingent COLA:\nfunded ratio",
		
		EEC_returnSmooth         = "Contingent EEC:\n5-year return",
		EEC_FR_t100              = "Contingent EEC:\nfunded ratio",
		
		EEC_sharedADCcap         = "Shared-ADC:\n10% cap",  
		EEC_sharedADC            = "Shared-ADC:\nno cap", 
		
		# hybrid_DB                = "Hybrid \nDB-DC"
		hybrid_DB_noLegacy       = "Hybrid \nDB-DC"
	)


runs_paper_FR100 <- runs_paper
names(runs_paper_FR100) <- paste0(names(runs_paper_FR100), "_FR100")


results_paper <- 
	results_all %>% 
	filter(runname %in% c(names(runs_paper), names(runs_paper_FR100)))

```




## CAGR

```{r quintiles, echo = FALSE, warning=FALSE}

# Grouping variables

## Grouping by 40-year compound return 

# Dividing simulations into 5 groups based 40-year CAGR, difference in ERC rate:
#    1) 90th percentile and above []
#    2) 75th~90th percentile [)
#    3) 25th~75th percentile [)
#    4) 25th percentile and below [)
# Grouping can be done based on other variables (e.g. std of return)

get_CAGR <- function(df, span){

# span <- 40
	
df_CAGR <- 
results_all %>% 
	filter(runname == "baseline", sim >= 1, year <= span) %>% 
	group_by(sim) %>% 
	summarise(CAGR = get_geoReturn(i.r)) 
  #summarise(CAGR40 = sd(i.r)) 

grpVals_CAGR <-
	df_CAGR %>% 
	summarise(CAGR_pinf= Inf,
		        CAGR_q80 = quantile(CAGR, 0.80),
						CAGR_q60 = quantile(CAGR, 0.60),
						CAGR_q50 = quantile(CAGR, 0.50),
						CAGR_q40 = quantile(CAGR, 0.40),
						CAGR_q20 = quantile(CAGR, 0.20),
						CAGR_ninf= -Inf,
	) 

grpVals_CAGR_vector <- unlist(grpVals_CAGR[1,2:6])

df_CAGR %<>% 
	mutate(
		grp_CAGR = cut(CAGR, unlist(grpVals_CAGR[1,])[-4], label = F )
	)


#fn <- function(x){paste0(round(x * 100, 1), "%")}
fn <- function(x){paste0(sprintf("%.1f",x*100), "%")}



cutoff <- c(
	paste0("< ", fn(grpVals_CAGR_vector[5])),
	paste0(fn(grpVals_CAGR_vector[5]), "~" ,fn(grpVals_CAGR_vector[4])),
	paste0(fn(grpVals_CAGR_vector[4]), "~" ,fn(grpVals_CAGR_vector[2])),
	paste0(fn(grpVals_CAGR_vector[2]), "~" ,fn(grpVals_CAGR_vector[1])),
	paste0("> ", fn(grpVals_CAGR_vector[1]))
)

# cutoff

list(df     = df_CAGR, 
		 cutoff = cutoff)
}

df_CAGR40 <- get_CAGR(results_paper, 40)
df_CAGR30 <- get_CAGR(results_paper, 30)
df_CAGR15 <- get_CAGR(results_paper, 15)
df_CAGR26 <- get_CAGR(results_paper, 26)

```





# Analysis of ERC
```{r ERC_prep, echo=FALSE, warning=FALSE}

## PV ERC and EEC 
get_PVC <- function(df, span, dr = 0.075){

  df %>% 
	filter(year <= span) %>% 
	select(runname, runname_wlabel, sim, year, policy_type, ERC, EEC, UAAL) %>% 
	group_by(runname, sim) %>% 
	summarise(
		        runname_wlabel = unique(runname_wlabel),
						
		        # PV of ERC
		        ERC_PV         = sum(ERC / (1 + dr)^(year - 1)),
						ERCwUAAL_PV    = sum(ERC / (1 + dr)^(year - 1)) + UAAL[year == max(year)] / (1 + unique(dr))^(max(year) - 1),
						
						# PV of EEC
						EEC_PV         = sum(EEC / (1 + dr)^(year - 1))
						)
}

df_PVC_30y <- get_PVC(results_all, 30)
#df_PVC_40y <- get_PVC(results_all, 40)
#df_PVC_15y <- get_PVC(results_all, 15)



## Percentiles of PVC for each policy
get_PVC_qtiles <- function(df_PVC){

# df_PVC_qtiles <- 
	df_PVC %>% 
	filter(sim >= 1) %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						ERC_PV_q90 = quantile(ERC_PV, 0.90),
						ERC_PV_q75 = quantile(ERC_PV, 0.75),
						ERC_PV_q50 = quantile(ERC_PV, 0.50),
						ERC_PV_q25 = quantile(ERC_PV, 0.25),
						ERC_PV_q10 = quantile(ERC_PV, 0.1),
						
						ERCwUAAL_PV_q90 = quantile(ERCwUAAL_PV, 0.90, na.rm = TRUE),
						ERCwUAAL_PV_q75 = quantile(ERCwUAAL_PV, 0.75, na.rm = TRUE),
						ERCwUAAL_PV_q50 = quantile(ERCwUAAL_PV, 0.50, na.rm = TRUE),
						ERCwUAAL_PV_q25 = quantile(ERCwUAAL_PV, 0.25, na.rm = TRUE),
						ERCwUAAL_PV_q10 = quantile(ERCwUAAL_PV, 0.1,  na.rm = TRUE),
						
						EEC_PV_q90 = quantile(EEC_PV, 0.90),
						EEC_PV_q75 = quantile(EEC_PV, 0.75),
						EEC_PV_q50 = quantile(EEC_PV, 0.50),
						EEC_PV_q25 = quantile(EEC_PV, 0.25),
						EEC_PV_q10 = quantile(EEC_PV, 0.1)
						)
}


df_PVC_qtiles_30y <- get_PVC_qtiles(df_PVC_30y)
#df_PVC_qtiles_15y <- get_PVC_qtiles(df_PVC_15y)


## Maximum increase in ERC rate WITHIN 5 years

# Note:
#  - Need to take into account the possibility that the changes in less then 5 years
#    are greater than the 5-year change. The method below takes care of this. 



get_ERCMaxChg <- function(df, span){

df_ERCMaxChg <- 		
  df %>% 
  filter(sim >= 1, year <= span) %>% 
	select(runname, runname_wlabel, sim, year, policy_type, ERC_PR) %>%
	group_by(runname, sim) %>% 
	mutate(   ERC_PR_chg5y    = rollapply(ERC_PR, width = 6, get_nyearMax, fill = NA, align = "right")) %>% # zoo::rollapply
	summarise(runname_wlabel = unique(runname_wlabel),
		        ERC_PR_chg5yMax = max(ERC_PR_chg5y, na.rm = TRUE))
	
  df_ERCMaxChg_qtile <- 
	df_ERCMaxChg %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						ERC_PR_chg5yMax_q90 = quantile(ERC_PR_chg5yMax, 0.90),
						ERC_PR_chg5yMax_q75 = quantile(ERC_PR_chg5yMax, 0.75),
						ERC_PR_chg5yMax_q50 = quantile(ERC_PR_chg5yMax, 0.50),
						ERC_PR_chg5yMax_q25 = quantile(ERC_PR_chg5yMax, 0.25),
						ERC_PR_chg5yMax_q10 = quantile(ERC_PR_chg5yMax, 0.1)
						)	
  
  list(
  	ERCMaxChg = df_ERCMaxChg,
  	ERCMaxChg_qtile = df_ERCMaxChg_qtile
  )
}


df_ERCMaxChg_30y <- get_ERCMaxChg(results_all, 30)
#df_ERCMaxChg_15y <- get_ERCMaxChg(results_all, 15)



get_EECMaxChg <- function(df, span){

df_EECMaxChg <- 		
  df %>% 
  filter(sim >= 1, year <= span) %>% 
	select(runname, runname_wlabel, sim, year, policy_type, EEC_PR) %>%
	group_by(runname, sim) %>% 
	mutate(EEC_PR_chg5y    = rollapply(EEC_PR, width = 6, get_nyearMax, fill = NA, align = "right")) %>% # zoo::rollapply
	summarise(runname_wlabel = unique(runname_wlabel),
		        EEC_PR_chg5yMax = max(EEC_PR_chg5y, na.rm = TRUE))
	
  df_EECMaxChg_qtile <- 
	df_EECMaxChg %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						EEC_PR_chg5yMax_q90 = quantile(EEC_PR_chg5yMax, 0.90),
						EEC_PR_chg5yMax_q75 = quantile(EEC_PR_chg5yMax, 0.75),
						EEC_PR_chg5yMax_q50 = quantile(EEC_PR_chg5yMax, 0.50),
						EEC_PR_chg5yMax_q25 = quantile(EEC_PR_chg5yMax, 0.25),
						EEC_PR_chg5yMax_q10 = quantile(EEC_PR_chg5yMax, 0.1)
						)	
  
  list(
  	EECMaxChg = df_EECMaxChg,
  	EECMaxChg_qtile = df_EECMaxChg_qtile
  )
}

df_EECMaxChg_30y <- get_EECMaxChg(results_all, 30)
#df_EECMaxChg_15y <- get_EECMaxChg(results_all, 15)


df_PVC_30y %>% filter(runname == "hybrid_DB_noLegacy_FR100") 


```


## Table for PV ERC 
```{r tab_ERC_PV, echo = FALSE}




get_pvERC_tbl <- function(df_PVC, span = NULL, runs_select){

	
	# if(is.null(span)) span <- as.character(substitute(df_PVC)) %>% str_extract("\\d+")
	# select the df_PVC to use
	# df_PVC <- df_PVC_30y
	# span = 30

	df_CAGR <- get_CAGR(results_all, span)
	
	df_PVC %<>% filter(sim>=1) 
	
	ptiles_measure <- c(ptile90 = 0.9, ptile75 = 0.75, ptile50 = 0.50, ptile25 = 0.25, ptile10 = 0.1)
  nsim <- filter(df_PVC, sim >= 1, runname == "baseline") %>% nrow()
  fun_sum <- median
  
  
# # Percentiles of PV costs
df_PVC_ptiles <-
df_PVC %>%
	select(runname, sim, ERC_PV) %>%
	spread(runname, ERC_PV) %>%
	arrange(desc(baseline)) %>%
	mutate(sim_rank = 1:nsim) %>%
	filter(sim_rank %in% round(nsim*ptiles_measure)) %>%
	mutate(Percentile = names(ptiles_measure),
				 var = "ERC_PV") %>%
	select(var, Percentile, sim_rank, everything(), -sim) #sim_rank)
# df_PVC_ptiles


# extract PVC of baseline
df_PVC_baseline <- 
	filter(df_PVC, runname == "baseline") %>% 
	ungroup %>% select(sim, ERC_PV_baseline = ERC_PV)


# Diff PV costs by quintile
df_PVC_quintiles <-
	df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	left_join(df_PVC_baseline, by = "sim" ) %>% 
  left_join(df_CAGR$df, by = "sim") %>% 
	mutate(ERC_PV_std          = 100 * ERC_PV / df_PVC_ptiles$baseline[df_PVC_ptiles$Percentile == "ptile50"],
				 ERC_PV_std_baseline = 100 * ERC_PV_baseline / df_PVC_ptiles$baseline[df_PVC_ptiles$Percentile == "ptile50"],
		     ERC_PV_std_diff     = ERC_PV_std - ERC_PV_std_baseline,
				 ERC_PV_std_diff_pct = 100*( ERC_PV / ERC_PV_baseline - 1)
				 ) %>% 
	group_by(runname, grp_CAGR) %>% 
	summarise(ERC_PV_std          = fun_sum(ERC_PV_std),
						ERC_PV_std_diff     = fun_sum(ERC_PV_std_diff),
						ERC_PV_std_diff_pct = fun_sum(ERC_PV_std_diff_pct),
						ERC_PV              = fun_sum(ERC_PV)
						) %>% 
  arrange(runname, desc(grp_CAGR)) %>% 
	# For paper: standardize using the group 3 value of baseline
	ungroup %>% 
	mutate(ERC_PV_std = 100 * ERC_PV_std / ERC_PV_std[grp_CAGR == 3 & runname == "baseline"])



# Data for making tables
df_tab_ERC_PV <- 
df_PVC_quintiles %>% 
	select(runname, grp_CAGR , ERC_PV_std_diff_pct) %>% 
	spread(runname, ERC_PV_std_diff_pct) %>% 
	# select(grp_CAGR, one_of(runnames_show1)) %>% 
	left_join(df_PVC_quintiles %>%  # adding median baseline PV ERC in each group
							filter(runname == "baseline") %>% 
							ungroup() %>% 
							select(grp_CAGR, ERC_PV_std_baseline = ERC_PV_std), 
						by = "grp_CAGR") %>% 
	select(grp_CAGR, ERC_PV_std_baseline, everything(), -baseline) %>% 
	gather(policy, value, -grp_CAGR) %>% 
	# mutate(policy = factor(policy, levels = c("ERC_PV_baseline", runnames_show1),
	# 											         labels = c("PV employer cost\nin Baseline", runnames_show1_labels)),
	# 											 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, everything())
	# filter(grp_CAGR %in% c(1, 3, 5)) %>% 


df_tab_pvERC <- 
	df_tab_ERC_PV %>% 
	select(grp_CAGR, Return_Range, ERC_PV_std_baseline, one_of(names(runs_select))) %>% 
  gather(policy, value, -grp_CAGR, -Return_Range) %>% 
	mutate(policy = factor(policy, levels = c("ERC_PV_std_baseline", 	names(runs_select) ),
												         labels = c("PV employer cost\nin Baseline", 	runs_select)),
												 ) %>%
	spread(policy, value)
ncol_tab <- ncol(df_tab_pvERC)

tab_pvERC <- 
  df_tab_pvERC %>% 
	flextable() %>%
	add_header_row(values = paste0(span, "-year present value of employer contributions under different policies:\n Percentage differences from baseline by long-term return quintile\n (Median differences within quintiles)"), 
								 colwidths = ncol_tab) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = 1) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:ncol_tab, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:ncol_tab, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 1) %>% 
	set_header_labels(grp_CAGR = "Return\nquintile", 
										Return_Range = paste0("Range of ", span, "-year\ncompound returns"))
tab_pvERC


# pvERC values by quintile
df_tab_pvERC2 <- 
df_PVC_quintiles %>% 
	select(runname, grp_CAGR , ERC_PV) %>% 
	spread(runname, ERC_PV) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, one_of(names(runs_select)))


list(df        = df_tab_pvERC,
		 df_value  = df_tab_pvERC2,
		 tbl       = tab_pvERC)

}



tbl_pvERC_y30_FR75  <- get_pvERC_tbl(df_PVC_30y, 30, runs_paper)
#tbl_pvERC_y30_FR100 <- get_pvERC_tbl(df_PVC_30y, 30, runs_paper_FR100)


tbl_pvERC_y30_FR75$tbl
#tbl_pvERC_y30_FR100$tbl


save_as_image(tbl_pvERC_y30_FR75$tbl, path = paste0(dir_outputs, "tbl_quintile_ERCpv_y30_FR75.png"))


# xlsx::write.xlsx2(tbl_pvERC_y15$df, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_15y_diff")
# xlsx::write.xlsx2(tbl_pvERC_y15$df_value, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_15y_values", append = TRUE)
# xlsx::write.xlsx2(tbl_pvERC_y30$df, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_30y_diff", append = TRUE)
# xlsx::write.xlsx2(tbl_pvERC_y30$df_value, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_30y_values", append = TRUE)



```


## Table for ERC volatility
```{r tab_ERC_vol1, echo = FALSE}

# Function
get_ERCvol_tbl <- function(df, span = NULL, runnames_select){
  
	
	# df <- df_ERCMaxChg_30y$ERCMaxChg
	# span = 30
	 
	df_CAGR <- get_CAGR(results_all, span)
	


fun_sum <- median
# fun_sum <- mean

df_tab_ERC_vol <- 
  df %>% 
	select(runname, sim, ERC_PR_chg5yMax) %>% 
	mutate(ERC_PR_chg5yMax = 100 * ERC_PR_chg5yMax) %>% 
	left_join(df_CAGR$df, by = "sim") %>% 
	group_by(runname, grp_CAGR) %>% 
	summarise(ERC_PR_chg5yMax_med = fun_sum(ERC_PR_chg5yMax)) %>% 
  arrange(runname, desc(grp_CAGR)) %>% 
	#filter(runname %in% runnames_show1) %>% 
	spread(runname, ERC_PR_chg5yMax_med) %>% 
	# kable(digits = 1, caption = "Max 5-year ERC change in 40-year CAGR groups, starting FR=75%", format = 'pandoc')
	# gather(policy, value, -grp_CAGR40) %>% 
	# mutate(policy = factor(policy, levels = c(runnames_show1),
	# 											         labels = c(runnames_show1_labels)),
	# 											 ) %>% 
	# spread(policy, value) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, everything()) 


df_tab_ERC_vol <- 
  df_tab_ERC_vol %>% 
	# filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	gather(policy, value, -grp_CAGR, -Return_Range) %>% 
	filter(policy %in% names(runnames_select)) %>% 
	mutate(policy = factor(policy, levels = c(names(runnames_select)),
												         labels = c(runnames_select)),
												 ) %>%
	spread(policy, value)
	
	
	ncol_tab <- ncol(df_tab_ERC_vol)
	
	tab_ERC_vol <-  
	df_tab_ERC_vol%>% 
	flextable() %>%
	add_header_lines(values = paste0("Maximum increase in employer contribution rate in 5 years \nover a ", span, "-year period by long-term return quintile\n(Median values within groups)")) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = 1) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR = "Return\nquintile", 
										Return_Range = paste0("Range of ", span, "-year\ncompound returns")) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:ncol_tab, width = 1.5) %>% 
	colformat_num(j = 3:ncol_tab, digits = 1, suffix = "%") 

# tab_ERC_vol
  list(df  = df_tab_ERC_vol,
  		 tbl = tab_ERC_vol)
	
	
}



#tbl_ERCvol_y15 <- get_ERCvol_tbl(df_ERCMaxChg_15y$ERCMaxChg, 15)
tbl_ERCvol_y30_FR75 <- get_ERCvol_tbl(df_ERCMaxChg_30y$ERCMaxChg, 30, runs_paper)


#tbl_ERCvol_y15$tbl
tbl_ERCvol_y30_FR75$tbl


#save_as_image(tbl_ERCvol_y15$tbl, path = paste0(dir_outputs, "tbl_quintile_ERCvol_y15.png"))
save_as_image(tbl_ERCvol_y30_FR75$tbl, path = paste0(dir_outputs, "tbl_quintile_ERCvol_y30_FR75.png"))


# xlsx::write.xlsx2(tbl_ERCvol_y15$df, file = paste0(dir_outputs, "tbl_quintile_ERCvol.xlsx"), sheetName = "ERCvol_15y")
# xlsx::write.xlsx2(tbl_ERCvol_y30$df, file = paste0(dir_outputs, "tbl_quintile_ERCvol.xlsx"), sheetName = "ERCvol_30y", append = TRUE)


```

## Table for prob of ERC hike

```{r echo = FALSE}

df_ERC_hike <-  
  results_paper %>% 
	as_tibble() %>% 
	filter(sim >= 1) %>% 
	select(runname, sim, year, ERC_PR) %>% 
	group_by(runname, sim) %>% 
	mutate(ERC_hike = cumany( ERC_PR - lag(ERC_PR, 5, Inf) > 0.1) ) %>% 
	group_by(runname, year) %>% 
	summarise(ERC_hike = sum(ERC_hike)/n())

fig_title <- "Probability of ERC rate rising more than 10% \nwithin 5 years up to the given year"
df_ERC_hike %>% 
	filter(runname %in% names(runs_paper)) %>% 
	ggplot(aes(x = year, y = ERC_hike, color = runname)) +  
	geom_line() +
	geom_point() + 
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(7) )) + 
	scale_y_continuous(labels = function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 x = "Year",
			 y = "Probability",
			 color = "Policy"
			 )


tbl_ERChike_FR75 <- 
df_ERC_hike %>% 
	filter(runname %in% names(runs_paper), year %in% c(15, 30)) %>% 
	spread(runname, ERC_hike) %>% 
	gather(runname, value, -year) %>% 
	
  mutate(runname = factor(runname, levels = names(runs_paper),
												           labels = runs_paper)) %>% 
	spread(runname, value) %>% 
	
  gt(rowname_col = c("year")) %>% 
	fmt_percent(
    columns = 2:9,
    decimals = 1) %>% 
	tab_header(
    title = html("Probability of employer contribution rate rising more than 10%<br>within a 5-year period in the first 15 or 20 years")
  ) %>% 
	tab_stubhead(label = "Up to year")
tbl_ERChike_FR75

gtsave(tbl_ERChike_FR75, paste0(dir_outputs, "tbl_ERChike_FR75.png"))

	
```




# Analysis of EEC


## Table for PV EEC
```{r tab_ERC_PV, echo = FALSE}

# 
# runnames_pvERC_tbl  <- c(
# 		baseline                 = "Baseline",
# 		
# 		cola_returnSmooth_calib2     = "Contingent COLA:\n5-year return",
# 		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
# 		cola_FR_calib                = "Contingent COLA:\nfunded ratio",
# 		
# 		EEC_returnSmooth         = "Contingent EEC:\n5-year return",
# 		EEC_FR_t100              = "Contingent EEC:\nfunded ratio 100%",
# 		
# 		EEC_sharedADCcap         = "shared ADC\n 10% cap",  
# 		EEC_sharedADC            = "shared ADC\n no cap", 
# 		
# 		hybrid_DB                = "Hybrid \nDB-DC"
# 		#hybrid_DB_noLegacy       = "Hybrid \nDB-DC\nNo legacy cost",
# 	)
# 


get_pvEEC_tbl <- function(df_PVC, span = NULL, runs_select){

	
	# if(is.null(span)) span <- as.character(substitute(df_PVC)) %>% str_extract("\\d+")
	# select the df_PVC to use
	# df_PVC <- df_PVC_15y
	# span = 15

	df_CAGR <- get_CAGR(results_all, span)
	
	df_PVC %<>% filter(sim >= 1) 
	

	ptiles_measure <- c(ptile90 = 0.9, ptile75 = 0.75, ptile50 = 0.50, ptile25 = 0.25, ptile10 = 0.1)
  nsim <- filter(df_PVC, sim >= 1, runname == "baseline") %>% nrow()
  fun_sum <- median
  
  
# # Percentiles of PV costs
df_PVC_ptiles <-
df_PVC %>%
	select(runname, sim, EEC_PV) %>%
	spread(runname, EEC_PV) %>%
	arrange(desc(baseline)) %>%
	mutate(sim_rank = 1:nsim) %>%
	filter(sim_rank %in% round(nsim*ptiles_measure)) %>%
	mutate(Percentile = names(ptiles_measure),
				 var = "EEC_PV") %>%
	select(var, Percentile, sim_rank, everything(), -sim)
# df_PVC_ptiles



# Diff PV costs by quintile
df_PVC_quintiles <-
	df_PVC %>% 
	select(runname, sim, EEC_PV) %>% 
	left_join(filter(df_PVC, runname == "baseline") %>% ungroup %>% select(sim, EEC_PV_baseline = EEC_PV), by = "sim" ) %>% 
  left_join(df_CAGR$df, by = "sim") %>% 
	mutate(EEC_PV_std          = 100 * EEC_PV / df_PVC_ptiles$baseline[df_PVC_ptiles$Percentile == "ptile50"],
				 EEC_PV_std_baseline = 100 * EEC_PV_baseline / df_PVC_ptiles$baseline[df_PVC_ptiles$Percentile == "ptile50"],
		     EEC_PV_std_diff     = EEC_PV_std - EEC_PV_std_baseline,
				 EEC_PV_std_diff_pct = 100*( EEC_PV / EEC_PV_baseline - 1)
				 ) %>% 
	group_by(runname, grp_CAGR) %>% 
	summarise(EEC_PV_std          = fun_sum(EEC_PV_std),
						EEC_PV_std_diff     = fun_sum(EEC_PV_std_diff),
						EEC_PV_std_diff_pct = fun_sum(EEC_PV_std_diff_pct),
						EEC_PV              = fun_sum(EEC_PV)
						) %>% 
  arrange(runname, desc(grp_CAGR)) %>% 
	# For paper: standardize using the group 3 value of baseline
	ungroup %>% 
	mutate(EEC_PV_std = 100 * EEC_PV_std / EEC_PV_std[grp_CAGR == 3 & runname == "baseline"])




# Data for making tables
df_tab_EEC_PV <- 
df_PVC_quintiles %>% 
	select(runname, grp_CAGR , EEC_PV_std_diff_pct) %>% 
	spread(runname, EEC_PV_std_diff_pct) %>% 
	# select(grp_CAGR, one_of(runnames_show1)) %>% 
	left_join(df_PVC_quintiles %>%  # adding median baseline PV EEC in each group
							filter(runname == "baseline") %>% 
							ungroup() %>% 
							select(grp_CAGR, EEC_PV_std_baseline = EEC_PV_std), 
						by = "grp_CAGR") %>% 
	select(grp_CAGR, EEC_PV_std_baseline, everything(), -baseline) %>% 
	gather(policy, value, -grp_CAGR) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, everything())


df_tab_pvEEC <- 
	df_tab_EEC_PV %>% 
	select(grp_CAGR, Return_Range, EEC_PV_std_baseline, one_of(names(runs_select))) %>% 
  gather(policy, value, -grp_CAGR, -Return_Range) %>% 
	mutate(policy = factor(policy, levels = c("EEC_PV_std_baseline", 	names(runs_select) ),
												         labels = c("PV employer cost\nin Baseline", 	runs_select)),
												 ) %>%
	spread(policy, value)
ncol_tab <- ncol(df_tab_pvEEC)


tab_pvEEC <- 
  df_tab_pvEEC %>% 
	flextable() %>%
	add_header_row(values = paste0(span, "-year present value of employee contributions under different policies:\n Percentage differences from baseline by long-term return quintile\n (Median differences within quintiles)"), 
								 colwidths = ncol_tab) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:ncol_tab, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:ncol_tab, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 1) %>% 
	set_header_labels(grp_CAGR = "Return\nquintile", 
										Return_Range = paste0("Range of ", span, "-year\ncompound return"))
tab_pvEEC


# pvEEC values by quintile
df_tab_pvEEC2 <- 
df_PVC_quintiles %>% 
	select(runname, grp_CAGR , EEC_PV) %>% 
	spread(runname, EEC_PV) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, one_of(names(runs_select)))


list(df        = df_tab_pvEEC,
		 df_value  = df_tab_pvEEC2,
		 tbl       = tab_pvEEC)

}


tbl_pvEEC_y30_FR75  <- get_pvEEC_tbl(df_PVC_30y, 30, runs_paper[c(1, 4:7)])
#tbl_pvERC_y30_FR100 <- get_pvERC_tbl(df_PVC_30y, 30, runs_paper_FR100)


tbl_pvEEC_y30_FR75$tbl
#tbl_pvERC_y30_FR100$tbl



save_as_image(tbl_pvEEC_y30_FR75$tbl, path = paste0(dir_outputs, "tbl_quintile_EECpv_y30_FR75.png"))


# xlsx::write.xlsx2(tbl_pvERC_y15$df, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_15y_diff")
# xlsx::write.xlsx2(tbl_pvERC_y15$df_value, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_15y_values", append = TRUE)
# xlsx::write.xlsx2(tbl_pvERC_y30$df, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_30y_diff", append = TRUE)
# xlsx::write.xlsx2(tbl_pvERC_y30$df_value, file = paste0(dir_outputs, "tbl_quintile_ERCpv.xlsx"), sheetName = "pvERC_30y_values", append = TRUE)

```


## Table for EEC volatility
```{r tab_ERC_vol1, echo = FALSE}

# Function
get_EECvol_tbl <- function(df, span = NULL, runnames_select){
  
	
	# df <- df_EECMaxChg_30y$EECMaxChg
	# span = 30
	 
	df_CAGR <- get_CAGR(results_all, span)
	


fun_sum <- median
# fun_sum <- mean

df_tab_EEC_vol <- 
  df %>% 
	select(runname, sim, EEC_PR_chg5yMax) %>% 
	mutate(EEC_PR_chg5yMax = 100 * EEC_PR_chg5yMax) %>% 
	left_join(df_CAGR$df, by = "sim") %>% 
	group_by(runname, grp_CAGR) %>% 
	summarise(EEC_PR_chg5yMax_med = fun_sum(EEC_PR_chg5yMax)) %>% 
  arrange(runname, desc(grp_CAGR)) %>% 
	#filter(runname %in% runnames_show1) %>% 
	spread(runname, EEC_PR_chg5yMax_med) %>% 
	# kable(digits = 1, caption = "Max 5-year EEC change in 40-year CAGR groups, starting FR=75%", format = 'pandoc')
	# gather(policy, value, -grp_CAGR40) %>% 
	# mutate(policy = factor(policy, levels = c(runnames_show1),
	# 											         labels = c(runnames_show1_labels)),
	# 											 ) %>% 
	# spread(policy, value) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, everything()) 


df_tab_EEC_vol <- 
  df_tab_EEC_vol %>% 
	# filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	gather(policy, value, -grp_CAGR, -Return_Range) %>% 
	filter(policy %in% names(runnames_select)) %>% 
	mutate(policy = factor(policy, levels = c(names(runnames_select)),
												         labels = c(runnames_select)),
												 ) %>%
	spread(policy, value)
	
	
	ncol_tab <- ncol(df_tab_EEC_vol)
	
	tab_EEC_vol <-  
	df_tab_EEC_vol%>% 
	flextable() %>%
	# add_header_lines(values = paste0("Maximum increase in employee contribution rate in 5 years by long-term return quintile\n", span, "-year period\n(Median values within groups)")) %>% 
	add_header_lines(values = paste0("Maximum increase in employee contribution rate in 5 years \nover a ", span, "-year period by long-term return quintile\n(Median values within groups)")) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = 1) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR = "Return\nquintile", 
										Return_Range = paste0("Range of ", span, "-year\ncompound return")) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:ncol_tab, width = 1.5) %>% 
	colformat_num(j = 3:ncol_tab, digits = 1, suffix = "%") 

# tab_EEC_vol
  list(df  = df_tab_EEC_vol,
  		 tbl = tab_EEC_vol)
}



#tbl_EECvol_y15 <- get_EECvol_tbl(df_EECMaxChg_15y$EECMaxChg, 15)
tbl_EECvol_y30_FR75 <- get_EECvol_tbl(df_EECMaxChg_30y$EECMaxChg, 30, runs_paper[c(1, 4:7)])


#tbl_EECvol_y15$tbl
tbl_EECvol_y30_FR75$tbl


#save_as_image(tbl_EECvol_y15$tbl, path = paste0(dir_outputs, "tbl_quintile_EECvol_y15.png"))
save_as_image(tbl_EECvol_y30_FR75$tbl, path = paste0(dir_outputs, "tbl_quintile_EECvol_y30_FR75.png"))

# xlsx::write.xlsx2(tbl_ERCvol_y15$df, file = paste0(dir_outputs, "tbl_quintile_ERCvol.xlsx"), sheetName = "ERCvol_15y")
# xlsx::write.xlsx2(tbl_ERCvol_y30$df, file = paste0(dir_outputs, "tbl_quintile_ERCvol.xlsx"), sheetName = "ERCvol_30y", append = TRUE)


```





# Analysis of benefit
```{r benefit_prep, include = FALSE}

# Cohorts to examine:
	# Cohort 1: Retired at age 60 in year 1 (1 - 41)
	# Cohort 2: Retired at age 60 in year 15 (15- 55)
		#  - After the 15-year amortization period for the year-1 UAAL 

# Normalize the benefit at age 60 to 100. 
# Need qxm.r in decrement table 

load("Inputs/riskShaing_demographics_100y.RData")


get_benefit <- function(df, start_year, span = 41){


#start_year <- 1
#span       <- 41

if(span < 21) stop("span must be no less than 21")
if(max(results_all$year) < start_year + span - 1) stop("Time span exceeds the max year in data.")


## Create a model run with cola_actual = infl and append to results_all
df_colaFull <- 
  #results_all %>% 
  df %>% 
	filter(runname == "baseline") %>% 
	mutate(cola_actual = infl,
				 runname     = "cola_full")

## df of annual benefit payments and discount factors
df_benefit <- 
	bind_rows(df, df_colaFull) %>% 
	filter(year %in% (start_year + seq_len(span) - 1)) %>% 
	select(runname, runname_wlabel, policy_type, sim, year, cola_actual) %>% 
	group_by(runname, sim) %>% 
	mutate(age = seq_len(span) - 1 + 60 ) %>% 
	left_join(decrement %>% ungroup() %>% filter(ea == min(ea))  %>% select(age, qxm.r) , by = "age") %>% 
	mutate(qxm.r   = ifelse(age == max(age), 1, qxm.r),
				 fct_qxm = ifelse(age == 60, 1, lag(cumprod(1-qxm.r))),
				 fct_dr      = 1/(1 + dr)^(age - 60),
				 fct_dr_low  = 1/(1 + dr_low)^(age - 60),
				 B       = 100 * ifelse(age == 60, 1, lag(cumprod(1+cola_actual))),
				 B_real  = B / (1 + infl)^(age - 60),
				 B_real_chg5y = rollapply(B_real, width = 6, get_nyearMin, fill = NA, align = "right")
				 )


df_benefit_qtile <- 
	df_benefit %>%
	filter(sim >= 1) %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						B_PV_dr    = sum(B * fct_dr),
						B_PV_tot   = sum(B* fct_dr * fct_qxm),
						B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]		
	) %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						B_PV_dr_q90 = quantile(B_PV_dr, 0.90),
						B_PV_dr_q75 = quantile(B_PV_dr, 0.75),
						B_PV_dr_q50 = quantile(B_PV_dr, 0.50),
						B_PV_dr_q25 = quantile(B_PV_dr, 0.25),
						B_PV_dr_q10 = quantile(B_PV_dr, 0.1),
						
						B_PV_tot_q90 = quantile(B_PV_tot, 0.90),
						B_PV_tot_q75 = quantile(B_PV_tot, 0.75),
						B_PV_tot_q50 = quantile(B_PV_tot, 0.50),
						B_PV_tot_q25 = quantile(B_PV_tot, 0.25),
						B_PV_tot_q10 = quantile(B_PV_tot, 0.1),
						
						B_real_chg5yMin_q90 = quantile(B_real_chg5yMin, 0.90),
						B_real_chg5yMin_q75 = quantile(B_real_chg5yMin, 0.75),
						B_real_chg5yMin_q50 = quantile(B_real_chg5yMin, 0.50),
						B_real_chg5yMin_q25 = quantile(B_real_chg5yMin, 0.25),
						B_real_chg5yMin_q10 = quantile(B_real_chg5yMin, 0.1),
						
						B_real_age80_q90 = quantile(B_real_age80, 0.90),
						B_real_age80_q75 = quantile(B_real_age80, 0.75),
						B_real_age80_q50 = quantile(B_real_age80, 0.50),
						B_real_age80_q25 = quantile(B_real_age80, 0.25),
						B_real_age80_q10 = quantile(B_real_age80, 0.1)
						)

list(
	benefit       = df_benefit,
	benefit_qtile = df_benefit_qtile 
)

}


df_benefit_y30  <- get_benefit(results_all, start_year = 1, span = 30)


# df_benefit_y41  <- get_benefit(results_all, start_year = 1, span = 41)
# df_benefit_y26  <- get_benefit(results_all, start_year = 1, span = 26)

```


## Table for PV benefit
```{r tab_B_PV1, echo=FALSE}


runnames_benefit  <- c(
		baseline                 = "Baseline",
		
		cola_returnSmooth_calib2 = "Contingent COLA:\n5-year return",
		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		
		cola_FR_calib            = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 75%",
	  cola_FR_calib_FR100      = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 100%"
	)



# Note: this function only works for members retired in year 1, with a 40-year period
get_pvB_quintile <- function(df, span){

# df  = df_benefit_y26
# span = 26
	
df_CAGR <- get_CAGR(results_all, span)	
	
fun_sum <- median
# fun_sum <- mean

# df <- df_benefit_y1

df_benefit_PV <- 
	df$benefit %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						#B_PV       = sum(B* fct_dr * fct_qxm)
						B_PV       = sum(B* fct_dr)
						#B_PV      = sum(B* fct_dr * fct_qxm)
						# B_PV_tot_drLow   = sum(B* fct_dr_low * fct_qxm)
	)


df_pvB_diff_quintile <- 
  df_benefit_PV %>% 
	filter(sim > 0) %>% 
	select(-runname_wlabel) %>% 
	left_join(filter(df_benefit_PV, runname == "baseline") %>% ungroup %>% 
							select(sim, 
										 B_PV_baseline = B_PV
										 #B_PV_dr_baseline  = B_PV_dr),
										 #B_PV_tot_drLow_baseline = B_PV_tot_drLow), 
										 ),
						by = "sim"
						) %>% 
	left_join(df_CAGR$df, by = "sim") %>% 
	mutate(
		     #ERC_PV          = 100 * ERC_PV / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
				 #ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
		     B_PV_diff     = B_PV - B_PV_baseline,
				 B_PV_diff_pct = 100*( B_PV / B_PV_baseline - 1),
				 
				 # B_PV_dr_diff     = B_PV_dr - B_PV_dr_baseline,
				 # B_PV_dr_diff_pct = 100* (B_PV_dr / B_PV_dr_baseline - 1)
				 
				 #B_PV_tot_drLow_diff     = B_PV_tot_drLow - B_PV_tot_drLow_baseline,
				 #B_PV_tot_drLow_diff_pct = 100*( B_PV_tot_drLow / B_PV_tot_drLow_baseline - 1)
				 ) %>% 
	group_by(runname, grp_CAGR) %>% 
	summarise(B_PV          = fun_sum(B_PV),
						B_PV_diff     = fun_sum(B_PV_diff),
						B_PV_diff_pct = fun_sum(B_PV_diff_pct),
						B_PV          = fun_sum(B_PV)
						# B_PV_dr          = fun_sum(B_PV_dr),
						# B_PV_dr_diff     = fun_sum(B_PV_dr_diff),
						# B_PV_dr_diff_pct = fun_sum(B_PV_dr_diff_pct)
						
						# B_PV_tot_drLow          = fun_sum(B_PV_tot_drLow),
						# B_PV_tot_drLow_diff     = fun_sum(B_PV_tot_drLow_diff),
						# B_PV_tot_drLow_diff_pct = fun_sum(B_PV_tot_drLow_diff_pct)
						) %>% 
  arrange(runname, desc(grp_CAGR))


df_tab_pvB <- 
df_pvB_diff_quintile %>% 
	select(runname, grp_CAGR, B_PV_diff_pct) %>% 
	# 
	ungroup() %>% 
	# mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_PV_diff_pct) %>% 
	select(-baseline) %>% 
	left_join(df_pvB_diff_quintile %>% 
							filter(runname == "baseline") %>% 
							ungroup() %>% 
	            select(grp_CAGR, B_PV),
						by = "grp_CAGR"
						) %>% 
	select(baseline_PVB = B_PV, everything()) %>% 
#tab_pvB_quintile <- 
	gather(policy, value, -grp_CAGR) %>%
	filter(policy %in% c("baseline_PVB", names(runnames_benefit) )) %>% 
	mutate(policy = factor(policy, levels = c("baseline_PVB", names(runnames_benefit) ),
												         labels = c("PV benefit\nin Baseline", runnames_benefit)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range =df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, everything()) 

ncol_tab <- ncol(df_tab_pvB)


tab_pvB_quintile <- 
	df_tab_pvB %>% 
	flextable() %>%
	add_header_lines(values = "Present value of benefit over 30 years (age 60-89):\nPercentage differences from baseline by long-term return quintile\n(Median values within quintiles)") %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:ncol_tab, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:ncol_tab, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(grp_CAGR = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound returns")
# tab_pvB_quintile

# pvERC values by quintile
df_tab_pvB2 <- 
df_pvB_diff_quintile %>% 
	select(runname, grp_CAGR , B_PV) %>% 
	spread(runname, B_PV) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, one_of(names(runnames_benefit)))


list(
	df_pvB                = df_benefit_PV,
	#df_pvB_diff_quintile  = df_pvB_diff_quintile,
	df_tbl                = df_tab_pvB,  
	tbl                   = tab_pvB_quintile,
	df_values             = df_tab_pvB2 
)

}


tbl_pvB_y30 <- get_pvB_quintile(df_benefit_y30, 30)
#tbl_pvB_y26 <- get_pvB_quintile(df_benefit_y26, 26)

tbl_pvB_y30$tbl


save_as_image(tbl_pvB_y30$tbl, path = paste0(dir_outputs, "tbl_quintile_Bpv_y30.png"))
#save_as_image(tbl_pvB_y26$tbl, path = paste0(dir_outputs, "tbl_quintile_Bpv_y26.png"))

# 
# xlsx::write.xlsx2(tbl_pvB_y26$df_tbl, 
# 									file = paste0(dir_outputs, "tbl_quintile_Bpv.xlsx"), 
# 									sheetName = "pvB_y26")
# 
# xlsx::write.xlsx2(tbl_pvB_y26$df_values, 
# 									file = paste0(dir_outputs, "tbl_quintile_Bpv.xlsx"), 
# 									sheetName = "pvB_y26_values",
# 									append = TRUE)
# 
# 
# xlsx::write.xlsx2(tbl_pvB_y41$df_tbl, 
# 									file = paste0(dir_outputs, "tbl_quintile_Bpv.xlsx"), 
# 									sheetName = "pvB_y41",
# 									append = TRUE)
# 
# xlsx::write.xlsx2(tbl_pvB_y41$df_values, 
# 									file = paste0(dir_outputs, "tbl_quintile_Bpv.xlsx"), 
# 									sheetName = "pvB_y41_values",
# 									append = TRUE)




```


## Table for benefit volatility
```{r tab_B_vol1, echo = FALSE}



get_Bvol_quintile <- function(df, span){

# df = df_benefit_y41
# span = 41

fun_sum <- median

df_CAGR <- get_CAGR(results_all, span)	


df_Bvol <- 
df$benefit %>% 
	filter(sim > 0) %>% 
	# filter(runname %in% names(runnames_benefit)) %>% 
  summarise(B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE)
						# B_real_age80   = B_real[age == 80]
						) %>% 
	left_join(df_CAGR$df, by = "sim") %>% 
	group_by(runname, grp_CAGR) %>% 
	summarise(B_real_chg5yMin_med = fun_sum(B_real_chg5yMin)) %>% 
	arrange(runname, desc(grp_CAGR)) %>% 
	ungroup() %>% 
	spread(runname, B_real_chg5yMin_med) %>% 
	gather(policy, value, -grp_CAGR) %>% 
	# mutate(policy = factor(policy, levels = c("baseline", names(runnames_benefit)),
	# 											         labels = c("Baseline", runnames_benefit))
	# 											 ) %>% 
	spread(policy, value) %>% 
	#mutate(Return_Range = df_CAGR40$cutoff) %>% 
	select(grp_CAGR, everything()) 
	

df_tbl_Bvol <- 	
df_Bvol %>% 
	gather(policy, value, -grp_CAGR) %>% 
	filter(policy %in% names(runnames_benefit)) %>% 
	mutate(policy = factor(policy, levels = c("baseline", names(runnames_benefit)),
												         labels = c("Baseline", runnames_benefit)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = df_CAGR$cutoff) %>% 
	select(grp_CAGR, Return_Range, everything())
	
ncol_tab <- ncol(df_tbl_Bvol)	

tbl_Bvol <- 
  df_tbl_Bvol %>% 	
	flextable() %>%
	add_header_lines(values = "Maximum 5-year decreases in real benefit by long-term return quintile\n(Median values within quintiles)") %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound returns") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:ncol_tab, width = 1.5) %>% 
	colformat_num(j = 3:ncol_tab, digits = 1, suffix = "%") 
tbl_Bvol

list(
	df     = df_Bvol,
	df_tbl = df_tbl_Bvol,  
	tbl    = tbl_Bvol
)

}

tbl_Bvol_y30 <- get_Bvol_quintile(df_benefit_y30, 30)
# tbl_Bvol_y26 <- get_Bvol_quintile(df_benefit_y26, 26)

tbl_Bvol_y30$tbl


save_as_image(tbl_Bvol_y30$tbl, path = paste0(dir_outputs, "tbl_quintile_Bvol_y30.png"))
# save_as_image(tbl_Bvol_y41$tbl, path = paste0(dir_outputs, "tbl_quintile_Bvol_y41.png"))

# xlsx::write.xlsx2(tbl_Bvol_y26$df_tbl, 
# 									file = paste0(dir_outputs, "tbl_quintile_Bvol.xlsx"), 
# 									sheetName = "Bvol_y26")
# 
# xlsx::write.xlsx2(tbl_Bvol_y41$df_tbl, 
# 									file = paste0(dir_outputs, "tbl_quintile_Bvol.xlsx"), 
# 									sheetName = "Bvol_y41",
# 									append = TRUE)

```


## Table for prob of low pv benefit

```{r echo=FALSE}


runnames_benefit  <- c(
		baseline                 = "Baseline",
		
		cola_returnSmooth_calib2 = "Contingent COLA:\n5-year return",
		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		
		cola_FR_calib            = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 75%",
	  cola_FR_calib_FR100      = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 100%"
	)

df_benefit <- df_benefit_y30

df_benefit_PV <- 
	df_benefit$benefit %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						#B_PV       = sum(B* fct_dr * fct_qxm)
						B_PV       = sum(B* fct_dr)
						#B_PV      = sum(B* fct_dr * fct_qxm)
						# B_PV_tot_drLow   = sum(B* fct_dr_low * fct_qxm)
	)


df_low_pvB <- 
df_benefit_PV %>% 
	filter(sim >=1) %>% 
	# left_join(filter(df_benefit_PV, runname == "cola_full") %>% 
	# 						ungroup %>%  select(sim, B_PV_tot_full = B_PV_tot), by = "sim") %>% 
  left_join(filter(df_benefit_PV, runname == "baseline") %>% 
  						ungroup %>%  select(sim, B_PV_baseline = B_PV), by = "sim") %>% 
	mutate(#dif_full     = B_PV_tot / B_PV_tot_full,
				 dif_baseline = B_PV / B_PV_baseline
				 ) %>% 
	group_by(runname) %>% 
	summarise(#Low_pvB_full_pct90     = 100 * sum(dif_full     <= 0.9)/n(),
		      
						Low_pvB_baseline_pct90 = 100 * sum(dif_baseline <= 0.9)/n(),
						
						#Low_pvB_full_pct95     = 100 * sum(dif_full     <= 0.95)/n(),
						Low_pvB_baseline_pct95 = 100 * sum(dif_baseline <= 0.95)/n(),
						Low_pvB_baseline_pct100 = 100 * sum(dif_baseline <= 1)/n(),
						)

tbl_Bpv_probLow <- 
df_low_pvB %>% 
	filter(runname %in% names(runnames_benefit)) %>% 
	select(runname, contains("Low_pvB_baseline")) %>% 
	# mutate(runname = factor(runname, levels = namerunnames_show2)) %>% 
	gather(Measure, value, -runname) %>% 
	spread(runname, value) %>% 
	# kable(digits = 1, caption = "Probability (%) of PV benefit below 90%/95% of that in baseline (cola = 1.5%)", format = 'pandoc')
  gather(policy, value, -Measure) %>% 
	mutate(policy = factor(policy, levels = names(runnames_benefit),
												         labels = c(runnames_benefit)),
				 
				 Measure = factor(Measure, levels = c("Low_pvB_baseline_pct90", "Low_pvB_baseline_pct95", "Low_pvB_baseline_pct100"),
				 								           labels = c("Lower than 90% of Baseline", "Lower than 95% of Baseline", "Lower than 100% of Baseline")
				 								                     ),
				 value = value / 100
												 ) %>% 
	spread(policy, value) %>% 
	select(-Baseline) %>% 
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = c("Measure")) %>% 
	fmt_percent(
    columns = 2:4,
    decimals = 1) %>% 
	tab_header(
    title = html("Probability of present value of benefit below 90%, 95%, and 100% of the level in baseline"), 
    subtitle = "For members who retire at age 60 in year 1"
  ) %>% 
	tab_stubhead(label = "Measure")

tbl_Bpv_probLow

gtsave(tbl_Bpv_probLow, paste0(dir_outputs, "tbl_Bpv_probLow.png"))


```

## Table for prob of real benefit lower than starting level

```{r, echo = FALSE}

df_B_low <- 
df_benefit_y30$benefit %>% 
	as_tibble() %>% 
	select(runname, runname_wlabel, sim, year, B_real) %>% 
	group_by(runname, sim) %>% 
	mutate(B_lower90 = cumany(B_real < 90)) %>% 
	group_by(runname, year) %>% 
	summarise(B_lower90 = sum(B_lower90) /n())
	

fig_title <- "Probability of real benefit falling below 90% of starting benefit \nin any year up to a given year"
df_B_low %>%
	filter(runname %in% names(runnames_benefit)) %>%
	ungroup %>%
	mutate(runname = factor(runname, levels= names(runnames_benefit)) ) %>%
	ggplot(aes(x = year, y = B_lower90, color = runname)) +
	geom_line() +
	geom_point() +
	scale_color_manual(values = c("black", "grey50", brewer_pal(type = "qual", palette = "Paired")(6) )) +
	scale_y_continuous(labels = function(x) percent(x, accuracy = 1)) +
	labs(title = fig_title,
			 x = "Year",
			 y = "Probability",
			 color = "Policy"
			 )

tbl_B_real_probLow <- 
  df_B_low %>% 
 	filter(runname %in% names(runnames_benefit), year %in% c(15, 30)) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = names(runnames_benefit))) %>% 
	spread(runname, B_lower90) %>% 
	# kable(digits = 3, caption = "Probability of real benefit falling below 90% of starting benefit \nin any year up to year 10 and 20", format = "pandoc") %>% 
  gather(policy, value, -year) %>% 
	mutate(policy = factor(policy, levels = names(runnames_benefit),
												         labels = runnames_benefit)
												 ) %>% 
	spread(policy, value) %>% 
	# select(-Baseline) %>% 
  # kable(digits = 1, caption = "Median percentage difference from baseline by return group (%)", format = "pandoc")
  gt(rowname_col = c("year")) %>% 
	fmt_percent(
    columns = 2:5,
    decimals = 1) %>% 
	tab_header(
    title = html("Probability of real benefit falling below 90% of starting benefit<br>in any year up to year 15 or 30"),
    subtitle = "For members who retire at age 60 in year 1"
  ) %>% 
	tab_stubhead(label = "Up to year")

tbl_B_real_probLow

gtsave(tbl_B_real_probLow, paste0(dir_outputs, "tbl_B_real_probLow.png"))



# 
# df_B_lowest <- 
# df_benefit_y1 %>% 
# 	as_tibble() %>% 
# 	select(runname, runname_wlabel, sim, year, B_real) %>% 
# 	group_by(runname, sim) %>% 
# 	summarise(B_lowest = min(B_real)) %>% 
# 	summarise(B_lowest_q90 = quantile(B_lowest, 0.9),
# 						B_lowest_q50 = quantile(B_lowest, 0.5),
# 						B_lowest_q10 = quantile(B_lowest, 0.1)
# 						)
# 
# 
# df_B_lowest %>% 
# 	filter(runname %in% runnames_show2) %>% 
# 	ungroup %>%
# 	mutate(runname = factor(runname, levels= runnames_show2)) %>% 
# 	gather(Percentile, value, -runname) %>% 
# 	mutate(Percentile = factor(Percentile) %>% fct_inorder()) %>% 
# 	spread(runname, value) %>% 
# 	kable(digits = 1, caption = "Distribution of the lowest annual real benefit level in 40 years (100 in year 1)", format = 'pandoc')
# 	
	
```





## Figure: Distribution of 40-year COLA

```{r}


runnames_colaDist <- c(
	baseline                 = "Baseline",
		
	cola_returnSmooth_calib2  = "Contingent COLA:\n5-year return",
	cola_FR_calib            = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 75%",
	cola_FR_calib_FR100      = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 100%"
	
	#cola_SDRS                = "SDRS-like",
	#cola_SDRS_FR100          = "SDRS-like \nYear-1 funded ratio 100%"
	#DA_as                    = "Conditional \nindexation"
	)


get_colaDist <- function(df, start_year, span = 40){

# start_year = 1
# span = 40

year_span <- start_year + seq_len(span) - 1


# Distribution of 40-year COLA
df_cola <- 
	results_all %>% 
	filter(year %in% year_span) %>% 
	# filter(year %in% 16:55) %>% 
	filter(sim >= 1, runname %in% names(runnames_colaDist) ) %>% 
	group_by(runname, sim) %>%
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg  = prod(1 + cola_actual[-n()])^(1/(n() - 1)) - 1)


df_cola_qtiles <- 
	df_cola %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg_q10 = quantile(cola_avg, 0.1),
						cola_avg_q25 = quantile(cola_avg, 0.25),
						cola_avg_q50 = quantile(cola_avg, 0.50),
						cola_avg_q75 = quantile(cola_avg, 0.75),
						cola_avg_q90 = quantile(cola_avg, 0.90)
						)

fig_title    <- paste0("Distributions of ", span, "-year compound annual COLA \nunder different COLA policies")
fig_subtitle <- paste0("For members who retire in year ", start_year)
fig_cola_qtiles_calib <- 
	df_cola_qtiles %>% 
	mutate(runname = factor(runname, levels = names(runnames_colaDist) ,
													         labels = runnames_colaDist)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = cola_avg_q10,
							 		lower  = cola_avg_q25,
							 		middle = cola_avg_q50,
							 		upper  = cola_avg_q75,
							 		ymax   = cola_avg_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_cola_qtiles, runname == "baseline") %>% pull(cola_avg_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 0.025)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.005), labels = function(x) percent(x, accuracy = 0.1)) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,
			 x = NULL, 
			 y = "Compound annual COLA")
fig_cola_qtiles_calib

list(
	df_qtiles = df_cola_qtiles,
	fig = fig_cola_qtiles_calib
)

}


fig_colaDist <- get_colaDist(results_all, start_year = 1, span = 30)
fig_colaDist$fig

save_figure(fig_colaDist$fig, dir_outputs, w = 11, h = 7, scale = 0.8)


```




 
#-----
# Figures for stochastic runs


## Distribution of pvERC
```{r}

# Use df_PVC_qtiles_15/30y generated in section "Analysis ERC"

df_PVC_qtiles_y15_plot <- 
  df_PVC_qtiles_15y %>% 
	mutate_at(vars(-runname,-runname_wlabel), ~ 100 *./df_PVC_qtiles_15y$ERC_PV_q50[df_PVC_qtiles_15y$runname == "baseline"]) %>% 
	select(runname, contains("ERC_PV")) 
   

runnames_ERC <- c(
   	baseline                 = "Baseline",
		
		cola_returnSmooth_calib2     = "Contingent\nCOLA:\n5-year return",
		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		cola_FR_calib                = "Contingent\nCOLA:\nfunded ratio",
		
		EEC_returnSmooth         = "Contingent\nEEC:\n5-year return",
		# EEC_FR                   = "Contingent EEC:\nfunded ratio threshold 85%",
		EEC_FR_t100              = "Contingent\nEEC:\nfunded ratio",
		
		EEC_sharedADCcap         = "Shared-ADC\n 10% EEC cap",  
		EEC_sharedADC            = "Shared-ADC\n no EEC cap", 
		
		#hybrid_DB                = "Hybrid \nDB-DC",
		hybrid_DB_noLegacy       = "Hybrid \nDB-DC",
		cola_SDRS                = "SDRS-like",
		DA_as                    = "Conditional \nindexation"
		
)



df_PVC_qtiles_plot <- df_PVC_qtiles_y15_plot 
nyear_pvERC <- 15

fig_title    <- paste0("Distributions of the present value of ", nyear_pvERC, "-year employer contributions (ERC) \nunder different risk-sharing policies") 
 
fig_dist_pvERC_y15_all <- 
  df_PVC_qtiles_plot %>% 
  filter(runname %in% names(runnames_ERC)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_ERC), 
													         labels = runnames_ERC)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.4,
							 stat = "identity",
							 aes(ymin   = ERC_PV_q10,
							 	 	lower   = ERC_PV_q25,
							 		middle  = ERC_PV_q50,
							 		upper   = ERC_PV_q75,
							 		ymax    = ERC_PV_q90)) + 
	geom_hline(yintercept =
						 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
						 linetype = 2) +
  geom_vline(xintercept = c(1.5, 5.5), linetype = 3, color = "grey60", size = 1) + 	
  annotate("text", x = 3.5, y = 175, label = "Policies with modest adjustments to \ndefined-benefit plans") + 
  annotate("text", x = 8.2, y = 175, label = "More-complex \nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(0, 180)) + 
	scale_y_continuous(breaks = seq(0, 300, 20)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Present value of ERC") 
 
fig_dist_pvERC_y15_all
save_figure(fig_dist_pvERC_y15_all, dir_outputs, w = 11, h = 7, scale = 0.85)


```


## Distribution of max ERC increase
```{r}

df_ERCvol_qtiles_plot <- df_ERCMaxChg_15y$ERCMaxChg_qtile
#nyear <- 15

fig_title    <- paste0("Distributions of maximum increase in employer contribution rate in 5 years\n(15-year) period")
fig_dist_ERCvol_y15 <- 
  df_ERCvol_qtiles_plot %>% 
  filter(runname %in% names(runnames_ERC)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_ERC), 
													         labels = runnames_ERC)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.4,
							 stat = "identity",
							 aes(ymin   = ERC_PR_chg5yMax_q10,
							 	 	lower   = ERC_PR_chg5yMax_q25,
							 		middle  = ERC_PR_chg5yMax_q50,
							 		upper   = ERC_PR_chg5yMax_q75,
							 		ymax    = ERC_PR_chg5yMax_q90)) + 
	# geom_hline(yintercept =
	# 					 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
	# 					 linetype = 2) +
  geom_vline(xintercept = c(1.5, 5.5), linetype = 3, color = "grey60", size = 1) + 	
  annotate("text", x = 3.5, y = 0.18, label = "Policies with modest adjustments to \ndefined-benefit plans") + 
  
	annotate("text", x = 8, y = 0.18, label = "More-complex \nrisk-sharing policies")	+
	
  # coord_cartesian(ylim = c(0, 180)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels =  function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Increase in ERC as a percentage of payroll") 
 
fig_dist_ERCvol_y15
save_figure(fig_dist_ERCvol_y15, dir_outputs, w = 11, h = 7, scale = 0.85)


# SDRS-like included
fig_title    <- paste0("Maximum 5-year increase in employer contribution rate over 15 years\n(75th percentile)")
fig_dist_ERCvol_y15_barplot <- 
  df_ERCvol_qtiles_plot %>% 
  filter(runname %in% names(runnames_ERC)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_ERC), 
													         labels = runnames_ERC)) %>% 
	ggplot(aes(x = runname, y)) + 
	geom_bar(aes(y = ERC_PR_chg5yMax_q75), 
					 stat = "identity",
					 width = 0.5,
					 fill = RIG.blue) + 
	geom_hline(yintercept =
						 filter(df_ERCvol_qtiles_plot, runname == "baseline") %>% pull(ERC_PR_chg5yMax_q75),
						 linetype = 2) +
  geom_vline(xintercept = c(1.5, 5.5), linetype = 3, color = "grey60", size = 1) + 	
  annotate("text", x = 3.5, y = 0.17, label = "Policies with modest adjustments to \ndefined-benefit plans") + 
  
	annotate("text", x = 8, y = 0.17, label = "More-complex \nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(0, 0.18)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels =  function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Increase in ERC as a percentage of payroll") 
 
fig_dist_ERCvol_y15_barplot
save_figure(fig_dist_ERCvol_y15_barplot, dir_outputs, w = 11, h = 7, scale = 0.85)


# SDRS-like excluded
fig_title    <- paste0("Maximum 5-year increase in employer contribution rate over 15 years\n(75th percentile)")
fig_dist_ERCvol_y15_barplot2 <- 
  df_ERCvol_qtiles_plot %>% 
  filter(runname %in% names(runnames_ERC)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_ERC), 
													         labels = runnames_ERC)) %>% 
	filter(runname != "SDRS-like") %>% 
	ggplot(aes(x = runname, y)) + 
	geom_bar(aes(y = ERC_PR_chg5yMax_q75), 
					 stat = "identity",
					 width = 0.5,
					 fill = RIG.blue) + 
	geom_hline(yintercept =
						 filter(df_ERCvol_qtiles_plot, runname == "baseline") %>% pull(ERC_PR_chg5yMax_q75),
						 linetype = 2) +
  geom_vline(xintercept = c(1.5, 5.5), linetype = 3, color = "grey60", size = 1) + 	
  annotate("text", x = 3.5, y = 0.17, label = "Policies with modest adjustments to \ndefined-benefit plans") + 
  
	annotate("text", x = 8, y = 0.17, label = "More-complex \nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(0, 0.18)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels =  function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Increase in ERC as a percentage of payroll") 
 
fig_dist_ERCvol_y15_barplot2

save_figure(fig_dist_ERCvol_y15_barplot2, dir_outputs, w = 11, h = 7, scale = 0.85)

fig_dist_ERCvol_y15_barplot2_ppt <- fig_dist_ERCvol_y15_barplot2
save_figure(fig_dist_ERCvol_y15_barplot2_ppt, dir_outputs, w = 11, h = 7, scale = 0.75)



```


## Distribution of 40-year COLA

```{r}


runnames_colaDist <- c(
	baseline                 = "Baseline",
		
	cola_returnSmooth_calib2  = "Contingent COLA:\n5-year return",
	cola_FR_calib            = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 75%",
	cola_FR_calib_FR100      = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 100%"
	
	#cola_SDRS                = "SDRS-like",
	#cola_SDRS_FR100          = "SDRS-like \nYear-1 funded ratio 100%"
	#DA_as                    = "Conditional \nindexation"
	)



get_colaDist <- function(df, start_year, span = 40){

# start_year = 1
# span = 40

year_span <- start_year + seq_len(span) - 1


# Distribution of 40-year COLA
df_cola <- 
	results_all %>% 
	filter(year %in% year_span) %>% 
	# filter(year %in% 16:55) %>% 
	filter(sim >= 1, runname %in% names(runnames_colaDist) ) %>% 
	group_by(runname, sim) %>%
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg  = prod(1 + cola_actual[-n()])^(1/(n() - 1)) - 1)


df_cola_qtiles <- 
	df_cola %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg_q10 = quantile(cola_avg, 0.1),
						cola_avg_q25 = quantile(cola_avg, 0.25),
						cola_avg_q50 = quantile(cola_avg, 0.50),
						cola_avg_q75 = quantile(cola_avg, 0.75),
						cola_avg_q90 = quantile(cola_avg, 0.90)
						)

fig_title    <- "Distributions of 40-year compound annual COLA \nunder different COLA policies"
fig_subtitle <- paste0("For members who retire in year ", start_year)
fig_cola_qtiles_calib <- 
	df_cola_qtiles %>% 
	mutate(runname = factor(runname, levels = names(runnames_colaDist) ,
													         labels = runnames_colaDist)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = cola_avg_q10,
							 		lower  = cola_avg_q25,
							 		middle = cola_avg_q50,
							 		upper  = cola_avg_q75,
							 		ymax   = cola_avg_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_cola_qtiles, runname == "baseline") %>% pull(cola_avg_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 0.025)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.005), labels = function(x) percent(x, accuracy = 0.1)) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,
			 x = NULL, 
			 y = "Compound annual COLA")
fig_cola_qtiles_calib

list(
	df_qtiles = df_cola_qtiles,
	fig = fig_cola_qtiles_calib
)

}


fig_colaDist <- get_colaDist(results_all, start_year = 1)
fig_colaDist$fig

save_figure(fig_colaDist$fig, dir_outputs, w = 11, h = 7, scale = 0.8)


```


## Distribution of pv benefit
```{r}


runnames_pvB <- c(
	baseline                 = "Baseline",
		
	cola_returnSmooth_calib2  = "Contingent COLA:\n5-year return",
	cola_FR_calib            = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 75%",
	cola_FR_calib_FR100      = "Contingent COLA:\nfunded ratio\nYear-1 funded ratio 100%"
	
	#cola_SDRS                = "SDRS-like",
	#cola_SDRS_FR100          = "SDRS-like \nYear-1 funded ratio 100%"
	#DA_as                    = "Conditional \nindexation"
	)


fig_title    <- paste0("Distribution of the present value of benefit up to age 85 \nunder different risk-sharing policies")
fig_subtitle <- "Benefit at age 60 normalized to 100"
fig_dist_pvB_y26 <- 
  df_benefit_y26$benefit_qtile%>% 
  filter(runname %in% names(runnames_pvB)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_pvB), 
													         labels = runnames_pvB)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = B_PV_dr_q10,
							 	 	lower   = B_PV_dr_q25,
							 		middle  = B_PV_dr_q50,
							 		upper   = B_PV_dr_q75,
							 		ymax    = B_PV_dr_q90)) + 
	# geom_hline(yintercept =
	# 					 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
	# 					 linetype = 2) +
  # geom_vline(xintercept = c(1.5, 5.5), linetype = 3, color = "grey60", size = 1) + 	
#   annotate("text", x = 3.5, y = 0.18, label = "Policies with modest adjustments to \ndefined-benefit plans") + 
#   
# 	annotate("text", x = 8, y = 0.18, label = "More-complex \nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(1200, 1550)) + 
	scale_y_continuous(breaks = seq(0, 5000, 100), labels = comma) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,# fig_subtitle,
			 x = NULL, 
			 y = "Present value of benefit") 
 
fig_dist_pvB_y26
save_figure(fig_dist_pvB_y26, dir_outputs, w = 11, h = 7, scale = 0.8)



fig_title    <- paste0("Distribution of the present value of benefit up to age 85 \nunder different risk-sharing policies")
fig_subtitle <- "The present value under Baseline is normalized to 100"


B_PV_std <- df_benefit_y26$benefit_qtile[1, 5] %>% unlist

fig_dist_pvB_y26_std <- 
  df_benefit_y26$benefit_qtile%>% 
  filter(runname %in% names(runnames_pvB)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_pvB), 
													         labels = runnames_pvB)) %>% 
	mutate(across(c(-runname, -runname_wlabel), ~.x / B_PV_std * 100) ) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = B_PV_dr_q10,
							 	 	lower   = B_PV_dr_q25,
							 		middle  = B_PV_dr_q50,
							 		upper   = B_PV_dr_q75,
							 		ymax    = B_PV_dr_q90)) + 
	# geom_hline(yintercept =
	# 					 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
	# 					 linetype = 2) +
  # geom_vline(xintercept = c(1.5, 5.5), linetype = 3, color = "grey60", size = 1) + 	
#   annotate("text", x = 3.5, y = 0.18, label = "Policies with modest adjustments to \ndefined-benefit plans") + 
#   
# 	annotate("text", x = 8, y = 0.18, label = "More-complex \nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(85, 110)) + 
	scale_y_continuous(breaks = seq(0, 500, 5)) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,# fig_subtitle,
			 x = NULL, 
			 y = "Present value of benefit") 
 
fig_dist_pvB_y26_std
save_figure(fig_dist_pvB_y26_std, dir_outputs, w = 11, h = 7, scale = 0.8)

		


```

## Distribution of pvEEC

```{r}

# Use df_PVC_qtiles_15/30y generated in section "Analysis ERC"

df_pvEEC_qtiles_y15_plot <- 
  df_PVC_qtiles_15y %>% 
	mutate_at(vars(-runname,-runname_wlabel), ~ 100 *./df_PVC_qtiles_15y$EEC_PV_q50[df_PVC_qtiles_15y$runname == "baseline"]) %>% 
	select(runname, contains("EEC_PV")) 
   

runnames_EEC <- c(
   	baseline                 = "Baseline",
		
		#cola_returnSmooth_calib2     = "Contingent\nCOLA:\n5-year return",
		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		#cola_FR_calib                = "Contingent\nCOLA:\nfunded ratio",
		
		EEC_returnSmooth         = "Contingent\nEEC:\n5-year return",
		# EEC_FR                   = "Contingent EEC:\nfunded ratio threshold 85%",
		EEC_FR_t100              = "Contingent\nEEC:\nfunded ratio",
		
		EEC_sharedADCcap         = "shared ADC\n 10% EEC cap",  
		EEC_sharedADC            = "shared ADC\n no EEC cap", 
		
		#hybrid_DB                = "Hybrid \nDB-DC",
		#hybrid_DB_noLegacy       = "Hybrid \nDB-DC",
		cola_SDRS                = "SDRS-like"
		#DA_as                    = "Conditional \nindexation"
		
)



df_pvEEC_qtiles_plot <- df_pvEEC_qtiles_y15_plot
nyear_pvEEC <- 15

fig_title    <- paste0("Distributions of the present value of ", nyear_pvEEC, "-year employee contributions (EEC) \nunder different risk-sharing policies") 
 
fig_dist_pvEEC_y15_all <- 
  df_pvEEC_qtiles_plot %>% 
  filter(runname %in% names(runnames_EEC)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_EEC), 
													         labels = runnames_EEC)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.35,
							 stat = "identity",
							 aes(ymin   = EEC_PV_q10,
							 	 	lower   = EEC_PV_q25,
							 		middle  = EEC_PV_q50,
							 		upper   = EEC_PV_q75,
							 		ymax    = EEC_PV_q90)) + 
	geom_hline(yintercept =
						 filter(df_pvEEC_qtiles_plot, runname == "baseline") %>% pull(EEC_PV_q50),
						 linetype = 2) +
  geom_vline(xintercept = c(1.5, 3.5), linetype = 3, color = "grey60", size = 1) + 	
  annotate("text", x = 2.5, y = 315, label = "Policies with \nmodest adjustments to \ndefined-benefit plans") + 
  annotate("text", x = 5.2, y = 315, label = "More radical or more-complex\nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(0, 330)) + 
	scale_y_continuous(breaks = seq(0, 500, 50)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Present value of EEC") 
 
fig_dist_pvEEC_y15_all
save_figure(fig_dist_pvEEC_y15_all, dir_outputs, w = 11, h = 7, scale = 0.85)


```



## Distribution of max EEC increase

```{r}

df_EECvol_qtiles_plot <- df_EECMaxChg_15y$EECMaxChg_qtile
#nyear <- 15

# fig_title    <- paste0("Distributions of maximum increase in employer contribution rate in 5 years\n(15-year) period")
# fig_dist_ERCvol_y15 <- 
#   df_ERCvol_qtiles_plot %>% 
#   filter(runname %in% names(runnames_ERC)) %>% 
# 	mutate(runname = factor(runname, levels = names(runnames_ERC), 
# 													         labels = runnames_ERC)) %>% 
# 	ggplot(aes(x = runname)) + 
# 	geom_boxplot(width = 0.4,
# 							 stat = "identity",
# 							 aes(ymin   = ERC_PR_chg5yMax_q10,
# 							 	 	lower   = ERC_PR_chg5yMax_q25,
# 							 		middle  = ERC_PR_chg5yMax_q50,
# 							 		upper   = ERC_PR_chg5yMax_q75,
# 							 		ymax    = ERC_PR_chg5yMax_q90)) + 
# 	# geom_hline(yintercept =
# 	# 					 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
# 	# 					 linetype = 2) +
#   geom_vline(xintercept = c(1.5, 5.5), linetype = 3, color = "grey60", size = 1) + 	
#   annotate("text", x = 3.5, y = 0.18, label = "Policies with modest adjustments to \ndefined-benefit plans") + 
#   
# 	annotate("text", x = 8, y = 0.18, label = "More-complex \nrisk-sharing policies")	+
# 	
#   # coord_cartesian(ylim = c(0, 180)) + 
# 	scale_y_continuous(breaks = seq(0, 1, 0.05), labels =  function(x) percent(x, accuracy = 1)) + 
# 	labs(title = fig_title,
# 			 subtitle = NULL,# fig_subtitle,
# 			 x = NULL, 
# 			 y = "Increase in ERC as a percentage of payroll") 
#  
# fig_dist_ERCvol_y15
# save_figure(fig_dist_ERCvol_y15, dir_outputs, w = 11, h = 7, scale = 0.85)


fig_title    <- paste0("Maximum 5-year increase in employee contribution rate over 15 years\n(75th percentile)")
fig_dist_EECvol_y15_barplot <- 
  df_EECvol_qtiles_plot %>% 
  filter(runname %in% names(runnames_EEC)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_EEC), 
													         labels = runnames_EEC)) %>% 
	ggplot(aes(x = runname, y)) + 
	geom_bar(aes(y = EEC_PR_chg5yMax_q75), 
					 stat = "identity",
					 width = 0.5,
					 fill = RIG.blue) + 
	geom_hline(yintercept =
						 filter(df_EECvol_qtiles_plot, runname == "baseline") %>% pull(EEC_PR_chg5yMax_q75),
						 linetype = 2) +  


  geom_vline(xintercept = c(1.5, 3.5), linetype = 3, color = "grey60", size = 1) + 	
  annotate("text", x = 2.5, y = 0.17, label = "Policies with \nmodest adjustments to \ndefined-benefit plans") + 
  
	annotate("text", x = 5, y = 0.17, label = "More radical and more-complex \nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(0, 0.18)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels =  function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Increase in EEC as a percentage of payroll") 
 
fig_dist_EECvol_y15_barplot
save_figure(fig_dist_EECvol_y15_barplot, dir_outputs, w = 11, h = 7, scale = 0.85)



fig_title    <- paste0("Maximum 5-year increase in employee contribution rate over 15 years\n(75th percentile)")
fig_dist_EECvol_y15_barplot2 <- 
  df_EECvol_qtiles_plot %>% 
  filter(runname %in% names(runnames_EEC)) %>% 
	mutate(runname = factor(runname, levels = names(runnames_EEC), 
													         labels = runnames_EEC)) %>% 
	filter(runname != "SDRS-like") %>% 
	ggplot(aes(x = runname, y)) + 
	geom_bar(aes(y = EEC_PR_chg5yMax_q75), 
					 stat = "identity",
					 width = 0.5,
					 fill = RIG.blue) + 
	geom_hline(yintercept =
						 filter(df_EECvol_qtiles_plot, runname == "baseline") %>% pull(EEC_PR_chg5yMax_q75),
						 linetype = 2) +  


  geom_vline(xintercept = c(1.5, 3.5), linetype = 3, color = "grey60", size = 1) + 	
  annotate("text", x = 2.5, y = 0.17, label = "Policies with \nmodest adjustments to \ndefined-benefit plans") + 
  
	annotate("text", x = 5, y = 0.17, label = "More radical and more-complex \nrisk-sharing policies")	+
	
  coord_cartesian(ylim = c(0, 0.08)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.02), labels =  function(x) percent(x, accuracy = 1)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Increase in EEC as a percentage of payroll") 
 
fig_dist_EECvol_y15_barplot2
save_figure(fig_dist_EECvol_y15_barplot2, dir_outputs, w = 11, h = 7, scale = 0.8)


```




# Fitures for asset-shock runs
## Asset shock: ERC rate
```{r eval=FALSE}

## Deterministic asset shock scenarios:

# sim -1: starting FR = 100%
# sim -2: starting FR = 75%

df_assetShock <- 
	results_all %>% 
	filter(sim < 0)


runnames_shock <- c(
   	baseline                 = "Baseline",
		
		cola_returnSmooth_calib2     = "Contingent COLA:\n5-year return",
		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		cola_FR_calib                = "Contingent COLA:\nfunded ratio",
		
		EEC_returnSmooth         = "Contingent EEC:\n5-year return",
		# EEC_FR                   = "Contingent EEC:\nfunded ratio threshold 85%",
		EEC_FR_t100              = "Contingent EEC:\nfunded ratio",
		
		EEC_sharedADCcap         = "shared ADC\n 10% EEC cap",  
		EEC_sharedADC            = "shared ADC\n no EEC cap"
		
		#hybrid_DB                = "Hybrid \nDB-DC",
		#hybrid_DB_noLegacy       = "Hybrid \nDB-DC",
		#cola_SDRS                = "SDRS-like"
		#DA_as                    = "Conditional \nindexation"
)


df_assetShock_plot <- 
  df_assetShock %>% 
	filter(sim == -2, year <=20, runname %in% names(runnames_shock)) %>% # sim -2: 75% starting FR
	mutate(SC_PR = SC / PR) %>% 
	select(runname, sim, year,ERC, ERC_PR, FR_MA, NC_PR, EEC_PR, SC_PR, cola_actual) %>% 
	mutate(runname = factor(runname, names(runnames_shock)),
				 runname_label = factor(runname, labels = runnames_shock))

df_assetShock_plot %>% 
	filter(runname == "cola_returnSmooth_calib2")
	
df_assetShock_plot %>% 
	filter(runname == "cola_FR_calib")

df_assetShock_plot %>% 
	filter(runname == "EEC_sharedADC")


## ERC plot for policy guidebook


# Plotting ERC rate  

colors_plot <- brewer_pal(type = "qual", palette = "Paired")(8)

fig_title <- "Employer contribution rates after the asset shock\nunder different risk-sharing policies"

fig_shock_ERCpaper <- 
  df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% names(runnames_shock)[(1:8)]) %>% 
	mutate(Alpha = ifelse(runname %in% runnames_shock[(1)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
	annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) +
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(8) )) +
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) +
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") +
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2.5),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2.5)
				 )
fig_shock_ERCpaper


save_figure(fig_shock_ERCpaper, fig_folder = dir_outputs, scale = 0.95, w = 10, h = 6, dpi =400)
```




## Asset shock: EEC rate
```{r eval=FALSE}

## Deterministic asset shock scenarios:

# sim -1: starting FR = 100%
# sim -2: starting FR = 75%

df_assetShock <- 
	results_all %>% 
	filter(sim < 0)


runnames_shock <- c(
   	baseline                 = "Baseline",
		
		# cola_returnSmooth_calib2     = "Contingent COLA:\n5-year return",
		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		# cola_FR_calib                = "Contingent COLA:\nfunded ratio",
		
		EEC_returnSmooth         = "Contingent EEC:\n5-year return",
		# EEC_FR                   = "Contingent EEC:\nfunded ratio threshold 85%",
		EEC_FR_t100              = "Contingent EEC:\nfunded ratio",
		
		EEC_sharedADCcap         = "shared ADC\n 10% EEC cap",  
		EEC_sharedADC            = "shared ADC\n no EEC cap"
		
		#hybrid_DB                = "Hybrid \nDB-DC",
		#hybrid_DB_noLegacy       = "Hybrid \nDB-DC",
		#cola_SDRS                = "SDRS-like"
		#DA_as                    = "Conditional \nindexation"
)


df_assetShock_plot <- 
  df_assetShock %>% 
	filter(sim == -2, year <=20, runname %in% names(runnames_shock)) %>% # sim -2: 75% starting FR
	mutate(SC_PR = SC / PR) %>% 
	select(runname, sim, year,ERC, ERC_PR, FR_MA, NC_PR, EEC_PR, SC_PR, cola_actual) %>% 
	mutate(runname = factor(runname, names(runnames_shock)),
				 runname_label = factor(runname, labels = runnames_shock))

df_assetShock_plot %>% 
	filter(runname == "cola_returnSmooth_calib2")
	
df_assetShock_plot %>% 
	filter(runname == "cola_FR_calib")

df_assetShock_plot %>% 
	filter(runname == "EEC_sharedADC")


## ERC plot for policy guidebook


# Plotting ERC rate  

colors_plot <- brewer_pal(type = "qual", palette = "Paired")(8)

fig_title <- "Employee contribution rates after the asset shock\nunder different risk-sharing policies"

fig_shock_EECpaper <- 
  df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% names(runnames_shock)[(1:5)]) %>% 
	mutate(Alpha = ifelse(runname %in% runnames_shock[(1)], 1, 0)) %>% 
	ggplot(aes(x = year, y = EEC_PR, color = runname_label)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.19, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.19, label = "Recovery\n(12% annually)", color = "grey40") +
	annotate("text", x = 11, y = 0.19, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.2))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) +
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(8)[3:6] )) +
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) +
	labs(title = fig_title,
		   x = "Year",
			 y = "Employee contribution rate",
			 color = "Policy") +
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2.5),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2.5)
				 )
fig_shock_EECpaper


save_figure(fig_shock_EECpaper, fig_folder = dir_outputs, scale = 0.95, w = 10, h = 6, dpi =400)
```





## Asset shock: real benefit

```{r eval=FALSE}


load("Inputs/riskShaing_demographics_100y.RData")


runnames_shock_ben <- c(
   	baseline                 = "Baseline",
		
		cola_returnSmooth_calib2     = "Contingent COLA:\n5-year return",
		# cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
		cola_FR_calib                = "Contingent COLA:\nfunded ratio"
		
		#cola_FR_calib_FR100          = "Contingent\nCOLA:\nfunded ratio\n 100%"
		
		#EEC_returnSmooth         = "Contingent\nEEC:\n5-year return",
		# EEC_FR                   = "Contingent EEC:\nfunded ratio threshold 85%",
		#EEC_FR_t100              = "Contingent\nEEC:\nfunded ratio",
		
		#EEC_sharedADCcap         = "shared ADC\n 10% EEC cap",  
		#EEC_sharedADC            = "shared ADC\n no EEC cap"
		
		#hybrid_DB                = "Hybrid \nDB-DC",
		#hybrid_DB_noLegacy       = "Hybrid \nDB-DC",
		#cola_SDRS                = "SDRS-like"
		#DA_as                    = "Conditional \nindexation"
)

infl

df_benefit_det <- 
	results_all %>% 
	filter(sim == -2, year %in% 1:41) %>% 
	select(runname, policy_type, sim, year, cola_actual) %>% 
	group_by(runname, sim) %>% 
	mutate(age = 60:100) %>% 
	mutate(
				 B       = 100 * ifelse(age == 60, 1, lag(cumprod(1+cola_actual))),
				 B_real  = B / (1 + infl)^(age - 60)
				 ) %>% 
	filter(runname %in% names(runnames_shock_ben), year <= 15) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = names(runnames_shock_ben)),
				 runname_label = factor(runname, labels = runnames_shock_ben))



fig_title <- "Inflation-adjusted annual benefits after the asset shock\nunder different risk-sharing policies"
fig_subtitle <- "Benefit in year 1 = 100"

fig_shock_realB <- 
df_benefit_det %>% 
	filter(runname %in% names(runnames_shock_ben)[1:4]) %>% 
	ggplot(aes(x = year, y = B_real, color = runname_label)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -Inf, ymax = Inf, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -Inf, ymax = Inf, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 105, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 105, label = "Recovery\n(12% annually)", color = "grey40") +
  annotate("text", x = 11, y = 105, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
	coord_cartesian(ylim = c(60, 107))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) + 
	scale_y_continuous(breaks = seq(0, 200, 10)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) ))+
  scale_alpha_continuous(range = c(0.1,1), guide = FALSE) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,
		   x = "Year",
			 y = "Real annual benefit ",
			 color = "Policy") + 
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2.5),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2.5)
				 )
	
fig_shock_realB
save_figure(fig_shock_realB, fig_folder = dir_outputs, scale = 0.95, w = 10, h = 6, dpi =400)



results_all %>% 
	filter(sim == 0, runname == "EEC_sharedADC")


```




```{r}

results_all %>% 
	filter(runname %in% c("cola_returnSmooth_calib2", "cola_FR_calib"), sim == -3, year <=17) %>% 
	select(runname, sim, year, FR_MA, cola_actual)



# cola_returnSmooth_calib2 = "Contingent COLA:\n5-year return",
# 		cola_returnSmooth_calib2_s10 = "Contingent COLA:\n10-year return",
# 		cola_FR_calib            = "Contingent COLA:\nfunded ratio 100%",

```




