---
title: "Preparation for Policy Guidebook"
output: 
  html_notebook: 
    number_sections: yes
    toc: yes
    fig_caption: yes
editor_options: 
  chunk_output_type: console
---



```{r Global_settings, include=FALSE}

## Loading packages
source(here::here("libraries.R"))

theme_set(theme_yy())

# dir_modelResults <- paste0(here::here(),"/Outputs/")
dir_modelResults <- paste0(here::here(),"/Outputs_500sims/")
dir_outputs      <- paste0(here::here(),"/Outputs_Analysis/") 


# Global parameters for analysis
dr     <- 0.075 # discount rate
dr_low <- 0.03  # lower discount rate
infl  <- 0.02  # assumed inflation rate
Nyear <- 40    # Number of sim years for contribution analysis
cola_baseline <- 0.015

DC_EECrate <- 0.025
DC_ERCrate <- 0.028

# run names for policy runs to show in results
# policy_select <- c("baseline", 
# 									 "cola_return", "cola_returnSmooth", "cola_returnSmooth_calib",  
# 									 "cola_FR", "cola_FR_calib",  
# 									 "EEC_sharedADCfloor", "EEC_return", "EEC_returnSmooth", "EEC_FR", "hybrid_DB")


runnames_show_calib_labels <- c(
	baseline           = "Baseline",
	cola_return        = "Contingent COLA:\nReturn",
	cola_returnSmooth  = "Contingent COLA:\nReturn smoothed",
	cola_FR            = "Contingent COLA:\nFunded ratio",
	
	cola_returnSmooth_calib  = "Contingent COLA:\nReturn smoothed \ncalib",
	cola_FR_calib            = "Contingent COLA:\nFunded ratio \ncalib",
	
	#cola_returnSmooth_calib_FR100  = "Contingent COLA:\nReturn smoothed \ncalib FR100",
	#cola_FR_calib_FR100            = "Contingent COLA:\nFunded ratio \ncalib FR100",
	
	EEC_return         = "Contingent EEC:\nReturn",
	EEC_returnSmooth   = "Contingent EEC:\nReturn smoothed",
	EEC_FR             = "Contingent EEC:\nFunded ratio",
	
	hybrid_DB = "hybrid DB-DC",
	mixed_WRS = "WRS-like",
	cola_SDRS = "SDRS-like"
)
runnames_show_calib <- names(runnames_show_calib_labels)



runnames_cost1_labels <- c(
	baseline           = "Baseline",
	cola_return        = "Contingent COLA:\nReturn",
	cola_returnSmooth  = "Contingent COLA:\nReturn smoothed",
	cola_FR            = "Contingent COLA:\nFunded ratio",
	
	EEC_return         = "Contingent EEC:\nReturn",
	EEC_returnSmooth   = "Contingent EEC:\nReturn smoothed",
	EEC_FR             = "Contingent EEC:\nFunded ratio"
)
runnames_cost1 <- names(runnames_cost1_labels)



runnames_cost2_labels <- c(
	baseline           = "Baseline",

	cola_returnSmooth_calib  = "Contingent COLA:\nReturn smoothed \ncalib",
	cola_FR_calib            = "Contingent COLA:\nFunded ratio \ncalib",

	EEC_returnSmooth   = "Contingent EEC:\nReturn smoothed",
	EEC_FR             = "Contingent EEC:\nFunded ratio",
	
  hybrid_DB = "hybrid DB-DC",
	mixed_WRS = "WRS-like",
	cola_SDRS = "SDRS-like"
	
)
runnames_cost2 <- names(runnames_cost2_labels)




runnames_benefit1_labels <- c(
	baseline           = "Baseline",
	cola_return        = "Contingent COLA: \n return",
	cola_returnSmooth  = "Contingent COLA: \n return Smoothed",
	cola_FR            = "Contingent COLA: \n Funded ratio\nYear-1 funded ratio 75%",
  cola_FR_FR100      = "Contingent COLA: \n Funded ratio\nYear-1 funded ratio 100%"
)
runnames_benefit1 <- names(runnames_benefit1_labels)



runnames_benefit2_labels <- c(
	baseline           = "Baseline",

	cola_returnSmooth_calib  = "Contingent COLA: \n return Smoothed \ncalib",
	cola_FR_calib            = "Contingent COLA: \n Funded ratio\nYear-1 funded ratio 75%\ncalib",
	
	cola_FR_calib_FR100= "Contingent COLA: \n Funded ratio\nYear-1 funded ratio 100% \ncalib"
)
runnames_benefit2 <- names(runnames_benefit2_labels)


```


```{r Loading_results, include = FALSE}

source(here::here("Analysis_loadingResults.R"))
# Outputs: 
   # results_all
   # run_labels


```



# Calibration

```{r calib, echo = FALSE}

# Distribution of 40-year COLA with 75% initial funded ratio
df_cola <- 
	results_all %>% 
	filter(year %in% 1:40) %>% 
	# filter(year %in% 16:55) %>% 
	# filter(sim >= 1, str_detect(runname, "cola|baseline") ) %>% 
	group_by(runname, sim) %>%
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg  = prod(1 + cola_actual[-n()])^(1/(n() - 1)) - 1)

df_cola_qtiles <- 
	df_cola %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg_q10 = quantile(cola_avg, 0.1),
						cola_avg_q25 = quantile(cola_avg, 0.25),
						cola_avg_q50 = quantile(cola_avg, 0.50),
						cola_avg_q75 = quantile(cola_avg, 0.75),
						cola_avg_q90 = quantile(cola_avg, 0.90)
						)


df_cola_qtiles %>% 
	filter(runname %in% runnames_show_calib) 

df_cola_qtiles %>% 
	filter(runname %in% runnames_show_calib) %>% 
	mutate(runname = factor(runname, levels = runnames_show_calib,
													         labels = runnames_show_calib_labels)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = cola_avg_q10,
							 		lower  = cola_avg_q25,
							 		middle = cola_avg_q50,
							 		upper  = cola_avg_q75,
							 		ymax   = cola_avg_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_cola_qtiles, runname == "baseline") %>% pull(cola_avg_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 0.025)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.0025), labels = percent) + 
	labs(title = "Distribution of 40-year compound average COLA",
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Compound annual COLA")



```



```{r quintiles, echo = FALSE, warning=FALSE}

# Grouping variables

## Grouping by 40-year compound return 

# Dividing simulations into 5 groups based 40-year CAGR, difference in ERC rate:
#    1) 90th percentile and above []
#    2) 75th~90th percentile [)
#    3) 25th~75th percentile [)
#    4) 25th percentile and below [)
# Grouping can be done based on other variables (e.g. std of return)

df_CAGR40 <- 
results_all %>% 
	filter(runname == "baseline", sim >= 1) %>% 
	group_by(sim) %>% 
	summarise(CAGR40 = get_geoReturn(i.r)) 
  #summarise(CAGR40 = sd(i.r)) 

grpVals_CAGR40 <-
	df_CAGR40 %>% 
	summarise(CAGR40_pinf= Inf,
		        CAGR40_q90 = quantile(CAGR40, 0.80),
						CAGR40_q75 = quantile(CAGR40, 0.60),
						CAGR40_q50 = quantile(CAGR40, 0.50),
						CAGR40_q25 = quantile(CAGR40, 0.40),
						CAGR40_q10 = quantile(CAGR40, 0.20),
						CAGR40_ninf= -Inf,
	) 


grpVals_CAGR40_vector <- unlist(grpVals_CAGR40[1,2:6])

df_CAGR40 %<>% 
	mutate(
		grp_CAGR40 = cut(CAGR40, unlist(grpVals_CAGR40[1,])[-4], label = F )
		# grp_CAGR40 = case_when(
		# CAGR40 >= grpVals_CAGR40$CAGR40_q90 ~ 1,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q75 & CAGR40 < grpVals_CAGR40$CAGR40_q90 ~ 2,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q25 & CAGR40 < grpVals_CAGR40$CAGR40_q75 ~ 3,
		# CAGR40 >= grpVals_CAGR40$CAGR40_q10 & CAGR40 < grpVals_CAGR40$CAGR40_q25 ~ 4,
		# CAGR40 < grpVals_CAGR40$CAGR40_q10 ~ 5,
		# TRUE ~ NA_real_) 
	)


grp_CAGR40_labels <- c(
	"< 6.5%",
  "6.5%~7.2%",
  "7.2%~7.9%",
  "7.9%~8.6%",
  "> 8.6%"
)


```



# Analysis of ERC

```{r ERC_prep, echo = FALSE, warning=FALSE}

results_stch <-  
  results_all %>% 
	# filter(!str_detect(runname, "FR100")) %>% 
	# filter(sim >= 1, year %in% 21:40) 
	filter(sim >= 1, year <= Nyear) 


## PV ERC and EEC 
df_PVC <- 
  results_stch %>% 
	select(runname, runname_wlabel, sim, year, policy_type, ERC, EEC, UAAL) %>% 
	group_by(runname, sim) %>% 
	summarise(
		        runname_wlabel = unique(runname_wlabel),
						
		        # PV of ERC
		        ERC_PV         = sum(ERC / (1 + dr)^(year - 1)),
						ERCwUAAL_PV    = sum(ERC / (1 + dr)^(year - 1)) + UAAL[year == max(year)] / (1 + unique(dr))^(max(year) - 1),
						
						# PV of EEC
						EEC_PV         = sum(EEC / (1 + dr)^(year - 1))
						)
# df_PVC

## Percentiles of PVC for each policy
df_PVC_qtiles <- 
	df_PVC %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						ERC_PV_q90 = quantile(ERC_PV, 0.90),
						ERC_PV_q75 = quantile(ERC_PV, 0.75),
						ERC_PV_q50 = quantile(ERC_PV, 0.50),
						ERC_PV_q25 = quantile(ERC_PV, 0.25),
						ERC_PV_q10 = quantile(ERC_PV, 0.1),
						
						ERCwUAAL_PV_q90 = quantile(ERCwUAAL_PV, 0.90),
						ERCwUAAL_PV_q75 = quantile(ERCwUAAL_PV, 0.75),
						ERCwUAAL_PV_q50 = quantile(ERCwUAAL_PV, 0.50),
						ERCwUAAL_PV_q25 = quantile(ERCwUAAL_PV, 0.25),
						ERCwUAAL_PV_q10 = quantile(ERCwUAAL_PV, 0.1),
						
						EEC_PV_q90 = quantile(EEC_PV, 0.90),
						EEC_PV_q75 = quantile(EEC_PV, 0.75),
						EEC_PV_q50 = quantile(EEC_PV, 0.50),
						EEC_PV_q25 = quantile(EEC_PV, 0.25),
						EEC_PV_q10 = quantile(EEC_PV, 0.1)
						)

# df_PVC_qtiles
# Why PV ERC of SDRS is so low, even with final UAAL?


## distributions(percentiles of differences)

# df_PVC_sim2sim_m3 <- 
# 	df_PVC %>% 
# 	select(runname, sim, ERC_PV) %>% 
# 	left_join(filter(df_PVC, runname == "baseline") %>% ungroup() %>%  select(sim, ERC_PV_baseline = ERC_PV), by = "sim") %>% 
# 	mutate(diff_ERC_PV     = ERC_PV -  ERC_PV_baseline,
# 				 diff_ERC_PV_pct = 100* (ERC_PV / ERC_PV_baseline - 1)) %>% 
# 	group_by(runname) %>% 
# 	summarise(
# 		dff_ERC_PV_pct_q90 = quantile(diff_ERC_PV_pct, 0.90),
# 	  dff_ERC_PV_pct_q75 = quantile(diff_ERC_PV_pct, 0.75),
# 	  dff_ERC_PV_pct_q50 = quantile(diff_ERC_PV_pct, 0.50),
# 	  dff_ERC_PV_pct_q25 = quantile(diff_ERC_PV_pct, 0.25),
# 	  dff_ERC_PV_pct_q10 = quantile(diff_ERC_PV_pct, 0.10)
# 		) %>% 
# 	gather(Percentile, value, -runname) %>% 
# 	spread(runname, value) 


## Maximum increase in ERC rate WITHIN 5 years

# Note:
#  - Need to take into account the possibility that the changes in less then 5 years
#    are greater than the 5-year change. The method below takes care of this. 

# x <- filter(results_stch, sim ==1, runname == "cola_baseline") %>% pull("ERC_PR")
# zoo::rollapply(x, width = 6, get_nyearMax, fill = NA, align = "right")


df_ERCMaxChg <- 
	results_stch %>% 
	select(runname, runname_wlabel, sim, year, policy_type, ERC_PR) %>%
	group_by(runname, sim) %>% 
	mutate(   ERC_PR_chg5y    = rollapply(ERC_PR, width = 6, get_nyearMax, fill = NA, align = "right")) %>% # zoo::rollapply
	summarise(runname_wlabel = unique(runname_wlabel),
		        ERC_PR_chg5yMax = max(ERC_PR_chg5y, na.rm = TRUE))

# df_ERCMaxChg


df_ERCMaxChg_qtile <- 
	df_ERCMaxChg %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						ERC_PR_chg5yMax_q90 = quantile(ERC_PR_chg5yMax, 0.90),
						ERC_PR_chg5yMax_q75 = quantile(ERC_PR_chg5yMax, 0.75),
						ERC_PR_chg5yMax_q50 = quantile(ERC_PR_chg5yMax, 0.50),
						ERC_PR_chg5yMax_q25 = quantile(ERC_PR_chg5yMax, 0.25),
						ERC_PR_chg5yMax_q10 = quantile(ERC_PR_chg5yMax, 0.1)
						)
# df_ERCMaxChg_qtile


# Proability of ERC rate rising by more than 5% in 40 years
```



## Distributions of PV costs

```{r, warning=FALSE, echo = FALSE}

# df_PVC_qtiles %>% 
# 	mutate_at(vars(-runname,-runname_wlabel), ~ 100 * . / df_PVC_qtiles$ERC_PV_q50[df_PVC_qtiles$runname == "baseline"]) %>% 
# 	select(runname, contains("ERC_PV")) %>% 
# 	filter(runname %in% runnames_cost1) %>% 
# 	mutate(runname = factor(runname, levels = runnames_cost1)) %>% 
# 	gather(Percentile, value, -runname) %>% 
# 	mutate(Percentile = factor(Percentile) %>% fct_inorder()) %>% 
# 	spread(runname, value) %>% 
# 	kable(digits = 1, caption = "Percentiles of normalized PV ERC within each policy", format = "pandoc")


fig_title    <- "Distributions of the present value 40-year employer contribution \nunder different COLA policies"
df_PVC_qtiles_plot <- 
  df_PVC_qtiles %>% 
	mutate_at(vars(-runname,-runname_wlabel), ~ 100 * . / df_PVC_qtiles$ERC_PV_q50[df_PVC_qtiles$runname == "baseline"]) %>% 
	select(runname, contains("ERC_PV")) 
	# filter(runname %in% runnames_cost2) %>% 
	# mutate(runname = factor(runname, levels = runnames_cost2, 
	# 												         labels = runnames_cost2_labels)) 
  
# Original + smoothed
  fig_dist_cost1 <- 
  df_PVC_qtiles_plot %>% 
	filter(runname %in% runnames_cost1) %>% 
	mutate(runname = factor(runname, levels = runnames_cost1, 
													         labels = runnames_cost1_labels)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = ERC_PV_q10,
							 	 	lower   = ERC_PV_q25,
							 		middle  = ERC_PV_q50,
							 		upper   = ERC_PV_q75,
							 		ymax    = ERC_PV_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 200)) + 
	scale_y_continuous(breaks = seq(0, 300, 20)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Present value of ERC")

  
# Calibrated 
  fig_dist_cost2 <- 
  df_PVC_qtiles_plot %>% 
  filter(runname %in% runnames_cost2) %>% 
	mutate(runname = factor(runname, levels = runnames_cost2, 
													         labels = runnames_cost2_labels)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.4,
							 stat = "identity",
							 aes(ymin   = ERC_PV_q10,
							 	 	lower   = ERC_PV_q25,
							 		middle  = ERC_PV_q50,
							 		upper   = ERC_PV_q75,
							 		ymax    = ERC_PV_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_PVC_qtiles_plot, runname == "baseline") %>% pull(ERC_PV_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 200)) + 
	scale_y_continuous(breaks = seq(0, 300, 20)) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Present value of ERC")
  
  
  fig_dist_cost1
  fig_dist_cost2 
  	

```




## PV cost by quintile

**Cost Q1, Present value of ERC over 40 years compared to baseline: median differences in 5 return groups** 

```{r tab_ERC_PV, echo = FALSE}

ptiles_measure <- c(ptile90 = 0.9, ptile75 = 0.75, ptile50 = 0.50, ptile25 = 0.25, ptile10 = 0.1)
nsim <- filter(df_PVC, runname == "baseline") %>% nrow()
fun_sum <- median

# Percentiles of PV costs
df_PVC_ptiles <- 
df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	spread(runname, ERC_PV) %>% 
	arrange(desc(baseline)) %>% 
	mutate(sim_rank = 1:nsim) %>% 
	filter(sim_rank %in% round(nsim*ptiles_measure)) %>% 
	mutate(Percentile = names(ptiles_measure),
				 var = "ERC_PV") %>% 
	select(var, Percentile, everything(), -sim, -sim_rank)
	

# Diff PV costs by quintile
df_PVC_quintiles <-
	df_PVC %>% 
	select(runname, sim, ERC_PV) %>% 
	left_join(filter(df_PVC, runname == "baseline") %>% ungroup %>% select(sim, ERC_PV_baseline = ERC_PV), by = "sim" ) %>% 
  left_join(df_CAGR40, by = "sim") %>% 
	mutate(ERC_PV          = 100 * ERC_PV / df_PVC_ptiles$baseline[df_PVC_ptiles$Percentile == "ptile50"],
				 ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_ptiles$baseline[df_PVC_ptiles$Percentile == "ptile50"],
		     ERC_PV_diff     = ERC_PV - ERC_PV_baseline,
				 ERC_PV_diff_pct = 100*( ERC_PV / ERC_PV_baseline - 1)
				 ) %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PV          = fun_sum(ERC_PV),
						ERC_PV_diff     = fun_sum(ERC_PV_diff),
						ERC_PV_diff_pct = fun_sum(ERC_PV_diff_pct)
						) %>% 
  arrange(runname, desc(grp_CAGR40))


# Data for making tables
df_tab_ERC_PV <- 
df_PVC_quintiles %>% 
	select(runname, grp_CAGR40 , ERC_PV_diff_pct) %>% 
	spread(runname, ERC_PV_diff_pct) %>% 
	# select(grp_CAGR40, one_of(runnames_show1)) %>% 
	left_join(df_PVC_quintiles %>%  # adding median baseline PV ERC in each group
							filter(runname == "baseline") %>% 
							ungroup() %>% 
							select(grp_CAGR40, ERC_PV_baseline = ERC_PV), 
						by = "grp_CAGR40") %>% 
	select(grp_CAGR40, ERC_PV_baseline, everything(), -baseline) %>% 
	gather(policy, value, -grp_CAGR40) %>% 
	# mutate(policy = factor(policy, levels = c("ERC_PV_baseline", runnames_show1),
	# 											         labels = c("PV employer cost\nin Baseline", runnames_show1_labels)),
	# 											 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything())
	# filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	
# Table: no calibration + smoothed
tab_ERC_PV1 <- 
	df_tab_ERC_PV %>% 
	select(grp_CAGR40, Return_Range, ERC_PV_baseline, one_of(runnames_cost1)) %>% 
  gather(policy, value, -grp_CAGR40, -Return_Range) %>% 
	mutate(policy = factor(policy, levels = c("ERC_PV_baseline", runnames_cost1),
												         labels = c("PV employer cost\nin Baseline", runnames_cost1_labels)),
												 ) %>%
	spread(policy, value) %>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV employer contribution\n from baseline by long-term return quintile\n(Median values within groups)", 
								 colwidths = 9) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:9, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:9, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 1) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")
tab_ERC_PV1

# Calibrated
tab_ERC_PV2 <- 
	df_tab_ERC_PV %>% 
	select(grp_CAGR40, Return_Range, ERC_PV_baseline, one_of(runnames_cost2)) %>% 
  gather(policy, value, -grp_CAGR40, -Return_Range) %>% 
	mutate(policy = factor(policy, levels = c("ERC_PV_baseline", runnames_cost2),
												         labels = c("PV employer cost\nin Baseline", runnames_cost2_labels)),
												 ) %>%
	spread(policy, value)
	
	ncol_tab <- ncol(tab_ERC_PV2)
  
	tab_ERC_PV2 %<>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV employer contribution\n from baseline by long-term return quintile\n(Median values within groups)", 
								 colwidths = ncol_tab) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:ncol_tab, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:ncol_tab, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 1) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")

tab_ERC_PV2


tab_ERC_PV1
tab_ERC_PV2

# tab_ERC_PV
# save_as_image(tab_ERC_PV, path = here::here("Outputs_Analysis/tab_ERC_PV.png"))



```


## Volatility by quintile

```{r tab_ERC_vol1, echo = FALSE}

fun_sum <- median
# fun_sum <- mean

df_tab_ERC_vol1 <- 
df_ERCMaxChg %>% 
	select(runname, sim, ERC_PR_chg5yMax) %>% 
	mutate(ERC_PR_chg5yMax = 100 * ERC_PR_chg5yMax) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(ERC_PR_chg5yMax_med = fun_sum(ERC_PR_chg5yMax)) %>% 
  arrange(runname, desc(grp_CAGR40)) %>% 
	#filter(runname %in% runnames_show1) %>% 
	spread(runname, ERC_PR_chg5yMax_med) %>% 
	# kable(digits = 1, caption = "Max 5-year ERC change in 40-year CAGR groups, starting FR=75%", format = 'pandoc')
	# gather(policy, value, -grp_CAGR40) %>% 
	# mutate(policy = factor(policy, levels = c(runnames_show1),
	# 											         labels = c(runnames_show1_labels)),
	# 											 ) %>% 
	# spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) 


tab_ERC_vol1 <- 
  df_tab_ERC_vol1 %>% 
	# filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	gather(policy, value, -grp_CAGR40, -Return_Range) %>% 
	filter(policy %in% runnames_cost1) %>% 
	mutate(policy = factor(policy, levels = c(runnames_cost1),
												         labels = c(runnames_cost1_labels)),
												 ) %>%
	spread(policy, value) %>% 
	flextable() %>%
	add_header_row(values = "Maximum increase in employer contribution rate in 5 years by long-term return quintile\n(Median values within groups)", 
								 colwidths = 9) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:9, width = 1.4) %>% 
	colformat_num(j = 3:9, digits = 1, suffix = "%") 
tab_ERC_vol1

# save_as_image(tab_ERC_vol1, path = here::here("Outputs_Analysis/tab_ERC_vol1.png"))


tab_ERC_vol1_calib <- 
  df_tab_ERC_vol1 %>% 
	# filter(grp_CAGR40 %in% c(1, 3, 5)) %>% 
	gather(policy, value, -grp_CAGR40, -Return_Range) %>% 
	filter(policy %in% runnames_cost2) %>% 
	mutate(policy = factor(policy, levels = c(runnames_cost2),
												         labels = c(runnames_cost2_labels)),
												 ) %>%
	spread(policy, value) 
  
  ncol_tab <- ncol(tab_ERC_vol1_calib)
  
  tab_ERC_vol1_calib %<>% 
	flextable() %>%
	add_header_row(values = "Maximum increase in employer contribution rate in 5 years by long-term return quintile\n(Median values within groups)", 
								 colwidths = ncol_tab) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:ncol_tab, width = 1.4) %>% 
	colformat_num(j = 3:ncol_tab, digits = 1, suffix = "%") 
tab_ERC_vol1_calib

tab_ERC_vol1
tab_ERC_vol1_calib


```

## Probability of cost hike

```{r tab_ERC_vol2, echo = FALSE}

df_ERC_hike <-  
  results_stch %>% 
	as_tibble() %>% 
	select(runname, sim, year, ERC_PR) %>% 
	group_by(runname, sim) %>% 
	mutate(ERC_hike = cumany( ERC_PR - lag(ERC_PR, 5, Inf) > 0.1) ) %>% 
	group_by(runname, year) %>% 
	summarise(ERC_hike = sum(ERC_hike)/n())


tab_ERC_vol2 <- 
df_ERC_hike %>% 
	filter(runname %in% runnames_cost1, year %in% c(10, 20)) %>% 
	spread(runname, ERC_hike) %>% 
	# kable(digits = 2, caption = "Probability of ERC rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years", format = "pandoc")
	gather(policy, value, -year) %>% 
	
  mutate(policy = factor(policy, levels = c(runnames_cost1),
												         labels = c(runnames_cost1_labels)),
				 value = value * 100) %>% 
	spread(policy, value) %>% 
	
	flextable() %>%
	add_header_row(values = "Probability of employer contribution rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years", 
								 colwidths = 8) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 1, height = .8) %>%
	height(part = "header", i = 2, height = 1) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2:8, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	colformat_num(j = 2:8, digits = 1, suffix = "%") %>% 
	set_header_labels(year = "Up to year"
									   )
tab_ERC_vol2
#save_as_image(tab_ERC_vol2, path = here::here("Outputs_Analysis/tab_ERC_vol2.png"))


tab_ERC_vol2_calib <- 
df_ERC_hike %>% 
	filter(runname %in% runnames_cost2, year %in% c(10, 20)) %>% 
	spread(runname, ERC_hike) %>% 
	# kable(digits = 2, caption = "Probability of ERC rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years", format = "pandoc")
	gather(policy, value, -year) %>% 
	
  mutate(policy = factor(policy, levels = c(runnames_cost2),
												         labels = c(runnames_cost2_labels)),
				 value = value * 100) %>% 
	spread(policy, value) 
	
	ncol_tab <- ncol(tab_ERC_vol2_calib)
	
	tab_ERC_vol2_calib %>% 
	flextable() %>%
	add_header_row(values = "Probability of employer contribution rate rising more than 10% \nwithin a 5-year period in the first 10 or 20 years", 
								 colwidths = ncol_tab) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 1, height = .8) %>%
	height(part = "header", i = 2, height = 1) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2:ncol_tab, width = 1.4) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	colformat_num(j = 2:ncol_tab, digits = 1, suffix = "%") %>% 
	set_header_labels(year = "Up to year"
									   )
tab_ERC_vol2_calib

	
```




# Analysis of Benefits


```{r benefit_prep, include = FALSE}

# Cohorts to examine:
	# Cohort 1: Retired at age 60 in year 1 (1 - 41)
	# Cohort 2: Retired at age 60 in year 15 (15- 55)
		#  - After the 15-year amortization period for the year-1 UAAL 

# Normalize the benefit at age 60 to 100. 
# Need qxm.r in decrement table 

load("Inputs/riskShaing_demographics_100y.RData")

## Create a model run with cola_actual = infl and append to results_all

df_colaFull <- 
  results_all %>% 
	filter(runname == "baseline") %>% 
	mutate(cola_actual = infl,
				 runname     = "cola_full")

df_benefit_y1 <- 
	bind_rows(results_all, df_colaFull) %>% 
	filter(sim >= 1, year %in% 1:41) %>% 
	select(runname, runname_wlabel, policy_type, sim, year, cola_actual) %>% 
	group_by(runname, sim) %>% 
	mutate(age = 60:100) %>% 
	left_join(decrement %>% ungroup() %>% filter(ea == min(ea))  %>% select(age, qxm.r) , by = "age") %>% 
	mutate(qxm.r   = ifelse(age == max(age), 1, qxm.r),
				 fct_qxm = ifelse(age == 60, 1, lag(cumprod(1-qxm.r))),
				 fct_dr      = 1/(1 + dr)^(age - 60),
				 fct_dr_low  = 1/(1 + dr_low)^(age - 60),
				 B       = 100 * ifelse(age == 60, 1, lag(cumprod(1+cola_actual))),
				 B_real  = B / (1 + infl)^(age - 60),
				 B_real_chg5y = rollapply(B_real, width = 6, get_nyearMin, fill = NA, align = "right")
				 )
# df_benefit_y1 


df_benefit_qtile_y1 <- 
	df_benefit_y1 %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						B_PV_dr    = sum(B * fct_dr),
						B_PV_tot   = sum(B* fct_dr * fct_qxm),
						B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]		
	) %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						
						B_PV_dr_q90 = quantile(B_PV_dr, 0.90),
						B_PV_dr_q75 = quantile(B_PV_dr, 0.75),
						B_PV_dr_q50 = quantile(B_PV_dr, 0.50),
						B_PV_dr_q25 = quantile(B_PV_dr, 0.25),
						B_PV_dr_q10 = quantile(B_PV_dr, 0.1),
						
						B_PV_tot_q90 = quantile(B_PV_tot, 0.90),
						B_PV_tot_q75 = quantile(B_PV_tot, 0.75),
						B_PV_tot_q50 = quantile(B_PV_tot, 0.50),
						B_PV_tot_q25 = quantile(B_PV_tot, 0.25),
						B_PV_tot_q10 = quantile(B_PV_tot, 0.1),
						
						B_real_chg5yMin_q90 = quantile(B_real_chg5yMin, 0.90),
						B_real_chg5yMin_q75 = quantile(B_real_chg5yMin, 0.75),
						B_real_chg5yMin_q50 = quantile(B_real_chg5yMin, 0.50),
						B_real_chg5yMin_q25 = quantile(B_real_chg5yMin, 0.25),
						B_real_chg5yMin_q10 = quantile(B_real_chg5yMin, 0.1),
						
						B_real_age80_q90 = quantile(B_real_age80, 0.90),
						B_real_age80_q75 = quantile(B_real_age80, 0.75),
						B_real_age80_q50 = quantile(B_real_age80, 0.50),
						B_real_age80_q25 = quantile(B_real_age80, 0.25),
						B_real_age80_q10 = quantile(B_real_age80, 0.1)
						)


# runs_benefit <- c("cola_full", "baseline", "cola_return", "cola_FR", "cola_SDRS", "cola_FR_FR100", "cola_SDRS_FR100")
# runs_benefit_lables <- c(
# 	"COLA equal to inflation",
# 	"Baseline \nYear-1 funded ratio 100%",
# 	"Contingent COLA: \nreturn",
# 	"Contingent COLA: \nFunded ratio threshold",
# 	"SDRS",
# 	"Contingent COLA: \nFunded ratio threshold\nYear-1 funded ratio 100%",
# 	"SDRS \nYear-1 funded ratio 100%"
# )
	

# Distribution of 40-year COLA with 75% initial funded ratio
df_cola <- 
	results_all %>% 
	filter(year %in% 1:40) %>% 
	# filter(year %in% 16:55) %>% 
	filter(sim >= 1, str_detect(runname, "cola|baseline") ) %>% 
	group_by(runname, sim) %>%
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg  = prod(1 + cola_actual[-n()])^(1/(n() - 1)) - 1)

df_cola_qtiles <- 
	df_cola %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						cola_avg_q10 = quantile(cola_avg, 0.1),
						cola_avg_q25 = quantile(cola_avg, 0.25),
						cola_avg_q50 = quantile(cola_avg, 0.50),
						cola_avg_q75 = quantile(cola_avg, 0.75),
						cola_avg_q90 = quantile(cola_avg, 0.90)
						)

```



## Distribution of 40-year compound COLA**

```{r dist_COLA, fig.width=8, echo = FALSE}

fig_title    <- "Distributions of 40-year compound annual COLA \nunder different COLA policies"
# fig_subtitle <- "Starting funded ratio: 75%"
fig_cola_qtiles_calib <- 
	df_cola_qtiles %>% 
	filter(runname %in% runnames_benefit2) %>% 
	mutate(runname = factor(runname, levels = runnames_benefit2,
													         labels = runnames_benefit2_labels)) %>% 
	ggplot(aes(x = runname)) + 
	geom_boxplot(width = 0.3,
							 stat = "identity",
							 aes(ymin   = cola_avg_q10,
							 		lower  = cola_avg_q25,
							 		middle = cola_avg_q50,
							 		upper  = cola_avg_q75,
							 		ymax   = cola_avg_q90)
	) + 
	geom_hline(yintercept =
						 filter(df_cola_qtiles, runname == "baseline") %>% pull(cola_avg_q50),
						 linetype = 2) +
	coord_cartesian(ylim = c(0, 0.025)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.0025), labels = percent) + 
	labs(title = fig_title,
			 subtitle = NULL,# fig_subtitle,
			 x = NULL, 
			 y = "Compound annual COLA")
fig_cola_qtiles_calib




```



## PV benefit by quinitle

```{r tab_B_PV1, echo=FALSE}

fun_sum <- median
# fun_sum <- mean

df_benefit_PV <- 
	df_benefit_y1 %>% 
	summarise(runname_wlabel = unique(runname_wlabel),
						# B_PV_dr    = sum(B * fct_dr),
						B_PV_tot    = sum(B* fct_dr * fct_qxm),
						B_PV_tot_drLow   = sum(B* fct_dr_low * fct_qxm)
	)


#df_PVB_sim2sim_grp <- 
df_PVB_diff_quintile <- 
  df_benefit_PV %>% 
	select(-runname_wlabel) %>% 
	left_join(filter(df_benefit_PV, runname == "baseline") %>% ungroup %>% 
							select(sim, B_PV_tot_baseline = B_PV_tot, B_PV_tot_drLow_baseline = B_PV_tot_drLow), by = "sim") %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	mutate(
		     #ERC_PV          = 100 * ERC_PV / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
				 #ERC_PV_baseline = 100 * ERC_PV_baseline / df_PVC_sim2sim$baseline[df_PVC_sim2sim$Percentile == "ptile50"],
		     B_PV_tot_diff     = B_PV_tot - B_PV_tot_baseline,
				 B_PV_tot_diff_pct = 100*( B_PV_tot / B_PV_tot_baseline - 1),
				 
				 B_PV_tot_drLow_diff     = B_PV_tot_drLow - B_PV_tot_drLow_baseline,
				 B_PV_tot_drLow_diff_pct = 100*( B_PV_tot_drLow / B_PV_tot_drLow_baseline - 1)
				 ) %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_PV_tot          = fun_sum(B_PV_tot),
						B_PV_tot_diff     = fun_sum(B_PV_tot_diff),
						B_PV_tot_diff_pct = fun_sum(B_PV_tot_diff_pct),
						
						B_PV_tot_drLow          = fun_sum(B_PV_tot_drLow),
						B_PV_tot_drLow_diff     = fun_sum(B_PV_tot_drLow_diff),
						B_PV_tot_drLow_diff_pct = fun_sum(B_PV_tot_drLow_diff_pct)
						) %>% 
  arrange(runname, desc(grp_CAGR40))


df_tab_B_PV1 <- 
df_PVB_diff_quintile %>% 
	select(runname, grp_CAGR40, B_PV_tot_diff_pct) %>% 
	# 
	ungroup() %>% 
	# mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_PV_tot_diff_pct) %>% 
	select(-baseline) %>% 
	left_join(df_PVB_diff_quintile %>% 
							filter(runname == "baseline") %>% 
							ungroup() %>% 
	            select(grp_CAGR40, B_PV_tot),
						by = "grp_CAGR40"
						) %>% 
	select(baseline_PVB = B_PV_tot, everything()) 


	
tab_B_PV1 <- 
	df_tab_B_PV1 %>% 
	gather(policy, value, -grp_CAGR40) %>%
	filter(policy %in% c("baseline_PVB", runnames_benefit1)) %>% 
	mutate(policy = factor(policy, levels = c("baseline_PVB", runnames_benefit1),
												         labels = c("PV benefit\nin Baseline", runnames_benefit1_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV benefit from baseline\nby long-term return quintile\n(Median values within groups)", 
								 colwidths = 7) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:7, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:7, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")
tab_B_PV1
# save_as_image(tab_B_PV1, path = here::here("Outputs_Analysis/tab_B_PV1.png"))


tab_B_PV1_calib <- 
	df_tab_B_PV1 %>% 
	gather(policy, value, -grp_CAGR40) %>%
	filter(policy %in% c("baseline_PVB", runnames_benefit2)) %>% 
	mutate(policy = factor(policy, levels = c("baseline_PVB", runnames_benefit2),
												         labels = c("PV benefit\nin Baseline", runnames_benefit2_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	flextable() %>%
	add_header_row(values = "Percentage differences in PV benefit from baseline\nby long-term return quintile\n(Median values within groups)", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	width(j = 3:6, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	colformat_num(j = 4:6, digits = 1, suffix = "%") %>% 
	colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return")
tab_B_PV1_calib


tab_B_PV1
tab_B_PV1_calib


```


## Probability of low PV benefit

```{r tab_B_PV2, echo=FALSE}

df_low_pvB <- 
df_benefit_PV %>% 
	left_join(filter(df_benefit_PV, runname == "cola_full") %>% 
							ungroup %>%  select(sim, B_PV_tot_full = B_PV_tot), by = "sim") %>% 
  left_join(filter(df_benefit_PV, runname == "baseline") %>% 
  						ungroup %>%  select(sim, B_PV_tot_baseline = B_PV_tot), by = "sim") %>% 
	mutate(dif_full     = B_PV_tot / B_PV_tot_full,
				 dif_baseline = B_PV_tot / B_PV_tot_baseline
				 ) %>% 
	group_by(runname) %>% 
	summarise(Low_pvB_full_pct90     = 100 * sum(dif_full     <= 0.9)/n(),
						Low_pvB_baseline_pct90 = 100 * sum(dif_baseline <= 0.9)/n(),
						
						Low_pvB_full_pct95     = 100 * sum(dif_full     <= 0.95)/n(),
						Low_pvB_baseline_pct95 = 100 * sum(dif_baseline <= 0.95)/n(),
						)


tab_B_PV2 <- 
df_low_pvB %>% 
	filter(runname %in% runnames_benefit1) %>% 
	select(runname, contains("Low_pvB_baseline")) %>% 
	mutate(runname = factor(runname, levels = runnames_benefit1)) %>% 
	gather(Measure, value, -runname) %>% 
	spread(runname, value) %>% 
	# kable(digits = 1, caption = "Probability (%) of PV benefit below 90%/95% of that in baseline (cola = 1.5%)", format = 'pandoc')
  gather(policy, value, -Measure) %>% 
	mutate(policy = factor(policy, levels = c(runnames_benefit1),
												         labels = c(runnames_benefit1_labels)),
				 
				 Measure = factor(Measure, levels = c("Low_pvB_baseline_pct90", "Low_pvB_baseline_pct95"),
				 								           labels = c("Lower than 90% of Baseline", "Lower than 95% of Baseline")
				 								                     ),
				 value = value
												 ) %>% 
	spread(policy, value) %>% 
	select(-Baseline) %>% 
  flextable() %>%
	add_header_row(values = "Probability of present value of benefit below 90% or 95% of the level in baseline", 
								 colwidths = 5) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 2) %>%
	width(j = 2:5, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	colformat_num(j = 2:5, digits = 1, suffix = "%") %>% 
	#colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(Measure = "Measure")

tab_B_PV2
#save_as_image(tab_B_PV2, path = here::here("Outputs_Analysis/tab_B_PV2.png"))

tab_B_PV2_calib <- 
df_low_pvB %>% 
	filter(runname %in% runnames_benefit2) %>% 
	select(runname, contains("Low_pvB_baseline")) %>% 
	mutate(runname = factor(runname, levels = runnames_benefit2)) %>% 
	gather(Measure, value, -runname) %>% 
	spread(runname, value) %>% 
	# kable(digits = 1, caption = "Probability (%) of PV benefit below 90%/95% of that in baseline (cola = 1.5%)", format = 'pandoc')
  gather(policy, value, -Measure) %>% 
	mutate(policy = factor(policy, levels = c(runnames_benefit2),
												         labels = c(runnames_benefit2_labels)),
				 
				 Measure = factor(Measure, levels = c("Low_pvB_baseline_pct90", "Low_pvB_baseline_pct95"),
				 								           labels = c("Lower than 90% of Baseline", "Lower than 95% of Baseline")
				 								                     ),
				 value = value
												 ) %>% 
	spread(policy, value) %>% 
	select(-Baseline) %>% 
  flextable() %>%
	add_header_row(values = "Probability of present value of benefit below 90% or 95% of the level in baseline", 
								 colwidths = 4) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .8) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	width(j = 1, width = 2) %>%
	width(j = 2:4, width = 1.5) %>%
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	# autofit(add_w = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	colformat_num(j = 2:4, digits = 1, suffix = "%") %>% 
	#colformat_num(j = 3, digits = 0) %>% 
	set_header_labels(Measure = "Measure")

tab_B_PV2_calib


tab_B_PV2
tab_B_PV2_calib


```



## Max 5-year benefit decrease by quintile

```{r tab_B_vol1, echo = FALSE}

fun_sum <- median

df_tab_B_vol1 <- 
df_benefit_y1 %>% 
  summarise(B_real_chg5yMin = min(B_real_chg5y, na.rm = TRUE),
						B_real_age80   = B_real[age == 80]) %>% 
	left_join(df_CAGR40, by = "sim") %>% 
	group_by(runname, grp_CAGR40) %>% 
	summarise(B_real_chg5yMin_med = fun_sum(B_real_chg5yMin)) %>% 
	arrange(runname, desc(grp_CAGR40)) %>% 
	
	# filter(runname %in% runnames_show2) %>% 
	
	ungroup() %>% 
	# mutate(runname = factor(runname, levels = runnames_show2)) %>% 
	spread(runname, B_real_chg5yMin_med) 
	# kable(digits = 1, caption = "Max 5-year decrease in benefit by 40-year CAGR group, starting FR=75%", format = 'pandoc')

	gather(policy, value, -grp_CAGR40) %>% 
	mutate(policy = factor(policy, levels = c("baseline", runnames_show2),
												         labels = c("Baseline", runnames_show2_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) 
	

tab_B_vol1 <-  
	df_tab_B_vol1 %>% 
	gather(policy, value, -grp_CAGR40) %>% 
	filter(policy %in% runnames_benefit1) %>% 
	mutate(policy = factor(policy, levels = c("baseline", runnames_benefit1),
												         labels = c("Baseline", runnames_benefit1_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	flextable() %>%
	add_header_row(values = "Maximum 5-year decreases in real benefit by long-term return quintile\n(Median values within groups)", 
								 colwidths = 7) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:7, width = 1.5) %>% 
	colformat_num(j = 3:7, digits = 1, suffix = "%") 

tab_B_vol1
# save_as_image(tab_B_vol1, path = here::here("Outputs_Analysis/tab_B_vol1.png"))



tab_B_vol1_calib <-  
	df_tab_B_vol1 %>% 
	gather(policy, value, -grp_CAGR40) %>% 
	filter(policy %in% runnames_benefit2) %>% 
	mutate(policy = factor(policy, levels = c("baseline", runnames_benefit2),
												         labels = c("Baseline", runnames_benefit2_labels)),
												 ) %>% 
	spread(policy, value) %>% 
	mutate(Return_Range = grp_CAGR40_labels) %>% 
	select(grp_CAGR40, Return_Range, everything()) %>% 
	flextable() %>%
	add_header_row(values = "Maximum 5-year decreases in real benefit by long-term return quintile\n(Median values within groups)", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	width(j = 1, width = 0.8) %>%
	width(j = 2, width = 1.8) %>%
	set_header_labels(grp_CAGR40 = "Return\nquintile", 
										Return_Range = "Range of 40-year\ncompound return") %>% 
	align(j = 1:2, align = "center", part = "all")  %>% 
	width(j = 3:6, width = 1.5) %>% 
	colformat_num(j = 3:6, digits = 1, suffix = "%") 
tab_B_vol1_calib


tab_B_vol1
tab_B_vol1_calib


```



## Probablity of low annual benefit

```{r, tab_B_vol2, echo = FALSE}

df_B_low <- 
df_benefit_y1 %>% 
	as_tibble() %>% 
	select(runname, runname_wlabel, sim, year, B_real) %>% 
	group_by(runname, sim) %>% 
	mutate(B_lower90 = cumany(B_real < 90)) %>% 
	group_by(runname, year) %>% 
	summarise(B_lower90 = sum(B_lower90) /n())


tab_B_vol2 <- 
df_B_low %>% 
	filter(runname %in% runnames_benefit1, year %in% c(10, 20)) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_benefit1)) %>% 
	spread(runname, B_lower90) %>% 
	# kable(digits = 3, caption = "Probability of real benefit falling below 90% of starting benefit \nin any year up to year 10 and 20", format = "pandoc") %>% 
  gather(policy, value, -year) %>% 
	mutate(policy = factor(policy, levels = c(runnames_benefit1),
												         labels = c(runnames_benefit1_labels)),
				 value = 100 * value
												 ) %>% 
	spread(policy, value) %>% 
	flextable() %>%
	add_header_row(values = "Probability of real benefit falling below 90% \nof starting benefit in any year up to year 10 or 20", 
								 colwidths = 6) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	width(j = 1, width = .8) %>%
	width(j = 2:6, width = 1.5) %>% 
	colformat_num(j = 2:6, digits = 1, suffix = "%") %>% 
	set_header_labels(year = "Up to year") 
tab_B_vol2 	

# save_as_image(tab_B_vol2, path = here::here("Outputs_Analysis/tab_B_vol2.png"))

tab_B_vol2_calib <- 
df_B_low %>% 
	filter(runname %in% runnames_benefit2, year %in% c(10, 20)) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_benefit2)) %>% 
	spread(runname, B_lower90) %>% 
	# kable(digits = 3, caption = "Probability of real benefit falling below 90% of starting benefit \nin any year up to year 10 and 20", format = "pandoc") %>% 
  gather(policy, value, -year) %>% 
	mutate(policy = factor(policy, levels = c(runnames_benefit2),
												         labels = c(runnames_benefit2_labels)),
				 value = 100 * value
												 ) %>% 
	spread(policy, value) %>% 
	flextable() %>%
	add_header_row(values = "Probability of real benefit falling below 90% \nof starting benefit in any year up to year 10 or 20", 
								 colwidths = 5) %>% 
	# autofit() %>% 
	height(part = "body",   height = .6) %>%
	height(part = "header", i = 2, height = 1) %>%
	height(part = "header", i = 1, height = .7) %>%
	hrule(rule = "exact", part = "all") %>%
	bg(part = "header", i = 2, bg = "gray90") %>% 
	fontsize(size = 14, part = "all") %>% 
	fontsize(size = 18, part = "header", i = 1) %>% 
	align(j = 1, align = "center", part = "all")  %>% 
	width(j = 1, width = .8) %>%
	width(j = 2:5, width = 1.5) %>% 
	colformat_num(j = 2:5, digits = 1, suffix = "%") %>% 
	set_header_labels(year = "Up to year") 
tab_B_vol2_calib

tab_B_vol2
tab_B_vol2_calib

```



# Deterministic asset shock scenario

```{r echo = FALSE}

## Deterministic asset shock scenarios:

# sim -1: starting FR = 100%
# sim -2: starting FR = 75%

df_assetShock <- 
	results_all %>% 
	filter(sim < 0)


runnames_show_det <- c("baseline", 
										
										  "cola_return", 
											"cola_returnSmooth", 
										  "cola_FR",
											# "cola_FRramp"
							
							        "EEC_return",
											"EEC_returnSmooth",
										  "EEC_FR"
										  
										  # "EEC_sharedADCfloor"
										  #"hybrid_DB"
										)
runnames_show_det_labels <- c(
	baseline           = "Baseline:\nNo risk-sharing",
	cola_return        = "Contingent COLA:\nReturn",
	cola_returnSmooth  = "Contingent COLA:\nReturn smoothed",
	cola_FR            = "Contingent COLA:\nFunded ratio",
	EEC_return         = "Contingent EEC:\nReturn",
	EEC_returnSmooth   = "Contingent EEC:\nReturn smoothed",
	EEC_FR             = "Contingent EEC:\nFunded ratio"
)



df_assetShock_plot <- 
  df_assetShock %>% 
	filter(sim == -2, year <=30, runname %in% runnames_show_det) %>% # sim -2: 75% starting FR
	mutate(SC_PR = SC / PR) %>% 
	select(runname, sim, year,ERC, ERC_PR, FR_MA, NC_PR, EEC_PR, SC_PR, cola_actual) %>% 
	mutate(runname = factor(runname, runnames_show_det),
				 runname_label = factor(runname, labels = runnames_show_det_labels))

# df_assetShock_plot


# Plotting ERC rate  

fig_title <- "Employer contribution rates after the asset shock\nunder different risk-sharing policies"

fig_shock_ERC1 <- 
  df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:7)]) %>% 
	mutate(Alpha = ifelse(runname %in% runnames_show_det[(1)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label)) +  #alpha = Alpha)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
	annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) +
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(6) )) +
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) +
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") +
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )
fig_shock_ERC1

fig_shock_ERC2 <- 
df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:5)]) %>% 
	mutate(alpha = ifelse(runname %in% runnames_show_det[(1:3)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label, alpha = alpha)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
  annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
	coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) )) + 
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) + 
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") + 
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )

fig_shock_ERC3 <- 
df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:5)]) %>% 
	mutate(alpha = ifelse(!runname %in% runnames_show_det[(2:3)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label, alpha = alpha)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
  annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) + 
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) ))+
  scale_alpha_continuous(range = c(0.1,1), guide = FALSE) + 
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") + 
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )

save_figure(fig_shock_ERC1, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)
save_figure(fig_shock_ERC2, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)
save_figure(fig_shock_ERC3, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)

fig_shock_ERC1
fig_shock_ERC2
fig_shock_ERC3


df_assetShock_plot %>% filter(year == 10)


df_assetShock_plot %>% 
	filter(year <=15) %>% 
	group_by(runname) %>% 
	summarise(ERC = sum(ERC / (1 + 0.075)^(year-1))) %>% 
	mutate(ERC_diff = ERC / ERC[runname == "baseline"] - 1 )




# Plotting FR rate  
df_assetShock_plot %>% 
	filter(year <=20) %>% 
	ggplot(aes(x = year, y = FR_MA, color = runname)) +
	geom_line() + 
	geom_point() + 
  coord_cartesian(ylim = c(0.5, 1))	+
	scale_y_continuous(breaks = seq(0, 1, 0.1), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) ))
# Note that baseline and EEC_FR have the same TOTAL contribution and therefore the same FR. 





load("Inputs/riskShaing_demographics_100y.RData")


df_benefit_det <- 
	results_all %>% 
	filter(sim == -2, year %in% 1:41) %>% 
	select(runname, runname_wlabel, policy_type, sim, year, cola_actual) %>% 
	group_by(runname, sim) %>% 
	mutate(age = 60:100) %>% 
	mutate(
				 B       = 100 * ifelse(age == 60, 1, lag(cumprod(1+cola_actual))),
				 B_real  = B / (1 + infl)^(age - 60)
				 ) %>% 
	filter(runname %in% runnames_show_det, year <= 15) %>% 
	ungroup() %>% 
	mutate(runname = factor(runname, levels = runnames_show_det),
				 runname_label = factor(runname, labels = runnames_show_det_labels))



fig_title <- "Inflation-adjusted annual benefits after the asset shock\nunder different risk-sharing policies"
fig_subtitle <- "Benefit in year 1 = 100"

fig_shock_realB <- 
df_benefit_det %>% 
	filter(runname %in% runnames_show_det[1:3]) %>% 
	ggplot(aes(x = year, y = B_real, color = runname_label)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -Inf, ymax = Inf, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -Inf, ymax = Inf, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 105, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 105, label = "Recovery\n(12% annually)", color = "grey40") +
  annotate("text", x = 11, y = 105, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
	coord_cartesian(ylim = c(60, 107))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) + 
	scale_y_continuous(breaks = seq(0, 200, 10)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) ))+
  scale_alpha_continuous(range = c(0.1,1), guide = FALSE) + 
	labs(title = fig_title,
			 subtitle = fig_subtitle,
		   x = "Year",
			 y = "Real annual benefit ",
			 color = "Policy") + 
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )
	
fig_shock_realB
save_figure(fig_shock_realB, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)





## ERC plot for paper


# Plotting ERC rate  

fig_title <- "Employer contribution rates after the asset shock\nunder different risk-sharing policies"

fig_shock_ERCpaper <- 
  df_assetShock_plot %>% 
	filter(year <= 15,
				 runname %in% runnames_show_det[(1:5)]) %>% 
	mutate(Alpha = ifelse(runname %in% runnames_show_det[(1)], 1, 0)) %>% 
	ggplot(aes(x = year, y = ERC_PR, color = runname_label)) +
	geom_line(size = 1) + 
	geom_point(size = 2) + 
	annotate("rect", xmin = 2, xmax = 3, ymin = -1, ymax = 1, fill = "red", size = 0, alpha = 0.1) +
	annotate("rect", xmin = 3, xmax = 6, ymin = -1, ymax = 1, fill = "yellow", size = 0, alpha = 0.1) +
	annotate("text", x = 2.5, y = 0.29, label = "Asset\nshock\n(-24%)", color = "grey40") +
	annotate("text", x = 4.5, y = 0.29, label = "Recovery\n(12% annually)", color = "grey40") +
	annotate("text", x = 11, y = 0.29, label = "Post-recovery\n(7.5% annually)", color = "grey40") +
  coord_cartesian(ylim = c(0, 0.3))	+
	scale_x_continuous(breaks = seq(0, 100, 1)) +
	scale_y_continuous(breaks = seq(0, 1, 0.05), labels = function(x) percent(x, accuracy = 1)) +
	scale_color_manual(values = c("black", brewer_pal(type = "qual", palette = "Paired")(4) )) +
  scale_alpha_continuous(range = c(0.15,1), guide = FALSE) +
	labs(title = fig_title,
		   x = "Year",
			 y = "Employer contribution rate",
			 color = "Policy") +
  guides(color = guide_legend(keywidth = 1.5, keyheight = 2),
				 shape = guide_legend(keywidth = 1.5, keyheight = 2)
				 )
fig_shock_ERCpaper


save_figure(fig_shock_ERCpaper, fig_folder = "Outputs_Analysis/", scale = 0.9, w = 10, h = 6, dpi =400)





```








